
---

```{r}
read.csv("GWAS_Results_Table.csv") %>% filter(SNP == "Lcu.2RBY.Chr4p46489391")
myG %>% filter(rs %in% c("Lcu.2RBY.Chr1p382800064", "Lcu.2RBY.Chr2p12871875"))
```

# Extra markers stuff

```{r eval = F, echo = F}
#
myMarkersd <- c("Lcu.2RBY.Chr2p42556949", "Lcu.2RBY.Chr5p1069654",  #
                "Lcu.2RBY.Chr6p2528817") #, "Lcu.2RBY.Chr6p307256203", "Lcu.2RBY.Chr5p1077484",

myMarkersh <- c("Lcu.2RBY.Chr1p2011396",  # stronger effect in temperate
                "Lcu.2RBY.Chr7p26181956") #
myMarkersh2 <- c("Lcu.2RBY.Chr1p2747812",
                 "Lcu.2RBY.Chr2p9922218",
                 "Lcu.2RBY.Chr2p68928307", 
                 "Lcu.2RBY.Chr6p166887344",
                 "Lcu.2RBY.Chr7p491811681")
#
myMarkersa <- c("Lcu.2RBY.Chr2p234027120", 
                "Lcu.2RBY.Chr7p528136791") # only an effect in italy!!!
myMarkersa2 <- c("Lcu.2RBY.Chr1p382800064",
                 "Lcu.2RBY.Chr1p454606728",
                 "Lcu.2RBY.Chr2p136778592",
                 "Lcu.2RBY.Chr3p286749559", 
                 "Lcu.2RBY.Chr4p6307024", 
                 "Lcu.2RBY.Chr5p474162648",
                 "Lcu.2RBY.Chr5p470514616",
                 "Lcu.2RBY.Chr6p378651008",
                 "Lcu.2RBY.Chr6p408908191",
                 "Lcu.2RBY.Chr7p5991114",
                 "Lcu.2RBY.Chr7p518235736")
#
myMarkersv <- c("Lcu.2RBY.Chr1p381072414", 
                "Lcu.2RBY.Chr1p323346547",
                "Lcu.2RBY.Chr2p8331384",
                "Lcu.2RBY.Chr3p19087338",
                "Lcu.2RBY.Chr3p27261184",
                "Lcu.2RBY.Chr5p473165246",
                "Lcu.2RBY.Chr6p36643693", 
                "Lcu.2RBY.Chr6p98578767")
#
myMarkersy <- c("Lcu.2RBY.Chr4p47546761", "Lcu.2RBY.Chr4p51863048",
                "Lcu.2RBY.Chr3p356016716", "Lcu.2RBY.Chr2p8161786",
                # Italy
                "Lcu.2RBY.Chr2p12871875", "Lcu.2RBY.Chr4p432747886",
                "Lcu.2RBY.Chr5p21201394", "Lcu.2RBY.Chr7p448380042")
myMarkersp <- c("Lcu.2RBY.Chr1p339778279",
                "Lcu.2RBY.Chr2p3372675",
                "Lcu.2RBY.Chr2p529777278",
                "Lcu.2RBY.Chr2p340566011",
                "Lcu.2RBY.Chr2p340566011",
                "Lcu.2RBY.Chr3p269524365",
                "Lcu.2RBY.Chr5p458058460",
                "Lcu.2RBY.Chr6p5228351")
                #"Lcu.2RBY.Chr6p182838436")
                #"Lcu.2RBY.Chr2p530433560", "Lcu.2RBY.Chr3p383438208", 
                #"Lcu.2RBY.Chr5p458058449") # this one is very good!!!!!!
myMarkerse <- c("Lcu.2RBY.Chr1p384688046",
                # h
                "Lcu.2RBY.Chr3p390779112", 
                "Lcu.2RBY.Chr4p343052519",
                "Lcu.2RBY.Chr5p1077484",
                # a
                "Lcu.2RBY.Chr2p136778592",
                "Lcu.2RBY.Chr3p256160240", 
                "Lcu.2RBY.Chr6p275594926",
                # V
                "Lcu.2RBY.Chr2p4504989", 
                "Lcu.2RBY.Chr2p14219576", # this one is high area in italy
                "Lcu.2RBY.Chr3p409868219", 
                "Lcu.2RBY.Chr4p2480676", # no effect in italy
                "Lcu.2RBY.Chr4p2949838",
                "Lcu.2RBY.Chr4p477030581",
                "Lcu.2RBY.Chr5p444371450",
                "Lcu.2RBY.Chr6p418901983",
                "Lcu.2RBY.Chr7p4127084", 
                "Lcu.2RBY.Chr7p480617781"
                #"Lcu.2RBY.Chr5p",
                
                )
# "Lcu.2RBY.Chr1p523664179", # not sure how I got this one, strong effect in temp
myMarkers <- c(myMarkersd, myMarkersh, myMarkersa)#, myMarkersp)
myMarkers_all <- c(myMarkers, myMarkersv, myMarkersy, myMarkersp, 
                   myMarkersh2, myMarkersa2)
myMColors <- c(rep("darkgreen",3), rep("darkblue",2), rep("darkred",2))#, rep("darkorange",3))
#
myMarkers <- c(myMarkersd, "Lcu.2RBY.Chr1p382800064", "Lcu.2RBY.Chr5p458058460")
myMarkers <- c(myMarkersd, "Lcu.2RBY.Chr2p3372665", "Lcu.2RBY.Chr3p269524365")
myMarkers <- c(myMarkersd, "Lcu.2RBY.Chr1p2610459", "Lcu.2RBY.Chr5p458058460")#"Lcu.2RBY.Chr4p46489391", "Lcu.2RBY.Chr7p491811681") #c("Lcu.2RBY.Chr2p12871875","Lcu.2RBY.Chr1p382800064"))
myMarkers <- c(myMarkersd, "Lcu.2RBY.Chr1p2011396","Lcu.2RBY.Chr7p528136791")
myMColors <- c(rep("darkgreen",3),  rep("darkred",2), rep("darkblue",1), rep("purple4",1))
```


```{r}
mp1 <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf=it17_f, 
                  markers1 = c("Lcu.2RBY.Chr2p12871875","Lcu.2RBY.Chr1p382800064"), 
                  markers2 = myMarkersd, mypchs = c(2,6,15:18), 
                  myTitle = "A) Metaponto, Italy 2017")
ggsave("additional/Markers/13_It_1.png", mp1,
         width = 9, height = 4, dpi = 600, bg = "white")
mp2 <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf=su17_f, 
                  markers1 = c("Lcu.2RBY.Chr2p12871875","Lcu.2RBY.Chr1p382800064"), 
                  markers2 = myMarkersd, mypchs = c(2,6,15:18),
                  myTitle = "B) Sutherland, Canada 2017")
ggsave("additional/Markers/13_It_2.png", mp2,
         width = 9, height = 4, dpi = 600, bg = "white")
myTitle <- paste0(paste(markers1, collapse = " & "), " = Sig Markers\n",
                  "\n", paste(markers2[1:2], collapse = " & "), " = Early DTF", 
                  "\n", markers2[3], " = Late DTF ")
mp <- ggarrange(mp1, mp2, ncol = 1, nrow = 2) %>%
  annotate_figure(bottom = title, fig.lab.pos = "bottom.right")
#
myMs1 <- c("Lcu.2RBY.Chr1p2011396", "")
mp1 <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf=it17_f, 
                  markers1 = myMs1, 
                  markers2 = myMarkersd, mypchs = c(2,6,15:18), 
                  myTitle = "A) Metaponto, Italy 2017")
ggsave("additional/Markers/13_It_5.png", mp1,
         width = 9, height = 4, dpi = 600, bg = "white")
mp2 <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf=su17_f, 
                  markers1 = myMs1, 
                  markers2 = myMarkersd, mypchs = c(2,6,15:18),
                  myTitle = "B) Sutherland, Canada 2017")
ggsave("additional/Markers/13_It_6.png", mp2,
         width = 9, height = 4, dpi = 600, bg = "white")
#
for(i in c(myMarkersh,myMarkersa,myMarkersv,myMarkersh2,myMarkersa2,myMarkersy)) {
  mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf = it17_f, 
                    markers1 = c("Lcu.2RBY.Chr1p2610459", i), markers2 = myMarkersd,
                    mypchs = c(2,6,15,15,17,17,18,18),
                  myTitle = "B) Italy 2017")
  ggsave(paste0("additional/Markers/14_Italy_",i,".png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
}
#
for(i in c(myMarkersh,myMarkersa,myMarkersv[-5],myMarkersh2,myMarkersa2,myMarkersy)) {
  mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf = it17_f, 
                    markers1 = c("Lcu.2RBY.Chr6p98578767", i), markers2 = myMarkersd,
                    mypchs = c(2,6,18,18,15,15),
                  myTitle = "B) Italy 2017")
  ggsave(paste0("additional/Markers/15_Italy_",i,".png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
}
for(i in c(myMarkersh,myMarkersa,myMarkersv,myMarkersh2,myMarkersa2,myMarkersy)) {
  mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf = it17_f, 
                    markers1 = c("Lcu.2RBY.Chr2p8331384", i), markers2 = myMarkersd,
                    mypchs = c(2,6,18,18,15,15),
                  myTitle = "B) Italy 2017")
  ggsave(paste0("additional/Markers/16_Italy_",i,".png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
}

mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf = it17_f, 
                    markers1 = c("Lcu.2RBY.Chr1p382800064", "Lcu.2RBY.Chr6p98578767"), 
                  markers2 = myMarkersd,
                    mypchs = c(2,6,18,18,15,15),
                  myTitle = "B) Italy 2017")
ggsave(paste0("additional/Markers/17_Italy_test.png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
#
myM1 <- c("Lcu.2RBY.Chr1p382800064", "Lcu.2RBY.Chr5p458058460")
myM1 <- c("Lcu.2RBY.Chr4p46489391",  "Lcu.2RBY.Chr1p2610459")#,"Lcu.2RBY.Chr2p8331384") # ,
myM1 <- c("Lcu.2RBY.Chr4p46489391", "Lcu.2RBY.Chr7p491811681")
#myM1 <- c( "Lcu.2RBY.Chr1p2610459", "Lcu.2RBY.Chr3p269524365")
mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf = it17_f, 
                    markers1 = myM1, 
                  markers2 = myMarkersd,
                    mypchs = c(2,6,18,18,15,15,1),
                  myTitle = "B) Italy 2017")
ggsave(paste0("additional/Markers/17_Italy_test.png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
mp <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf = su17_f, 
                    markers1 = myM1, 
                  markers2 = myMarkersd,
                    mypchs = c(2,6,18,18,15,15,1),
                  myTitle = "B) sut 2017")
ggsave(paste0("additional/Markers/17_sut_test.png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
#
myTs <- myTraits[grepl("Plot.Height|Plot.Area|Plot.Volume", myTraits)]
xx <- read.csv("GWAS_Results_Table.csv") %>%
  filter(Model != "MLMM") %>%
  filter(Trait %in% myTs) %>% 
  arrange(Effect)
```

---

```{r eval = F, echo = F}
x1 <- it17_f %>% select(Plot, Entry, Name, Trait, Value) %>% 
  spread(Trait, Value)
x2 <- it17_d %>% select(Plot, Entry, Name, Trait, Value_f) %>% 
  filter(Trait %in% c("crop_volume_m3_excess.green.based", 
                      "crop_area_m2_excess.green.based",
                      "mean_crop_height_m_excess.green.based") ) %>% 
  spread(Trait, Value_f)
```

# Closters AH

```{r}
x1 <- left_join(
  it17_gc.h[[2]] %>% select(Plot, Entry, Expt, Height=k),
  it17_gc.a[[2]] %>% select(Plot, Entry, Expt, Area=k),
  by = c("Plot", "Entry", "Expt"))
x2 <- left_join(
  su17_gc.h[[2]] %>% select(Plot, Entry, Expt, Height=k),
  su17_gc.a[[2]] %>% select(Plot, Entry, Expt, Area=k),
  by = c("Plot", "Entry", "Expt"))
xx <- bind_rows(x1, x2) %>%
  group_by(Expt, Entry) %>%
  summarise(Area = mean(Area, na.rm = T),
            Height = mean(Height, na.rm = T)) %>%
  left_join(select(myPCA, Entry, Cluster), by = "Entry")
mp1 <- ggplot(xx, aes(x = Area, y = Height, color = Cluster, alpha = Cluster)) +
  geom_point() +
  facet_grid(. ~ Expt) +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(1,0.1,0.1,0.1,0.1,0.1,0.1,1), guide = F) +
  theme_AGL +
  labs(y = "Plot Height", x = "Plot Area")
mp2 <- ggplot(xx, aes(x = Area, y = Height, color = Cluster, alpha = Cluster)) +
  geom_point() +
  facet_grid(. ~ Expt) +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.1,1,0.1,0.1,0.1,0.1,1,0.1), guide = F) +
  theme_AGL +
  labs(y = "Plot Height", x = "Plot Area")
mp3 <- ggplot(xx, aes(x = Area, y = Height, color = Cluster, alpha = Cluster)) +
  geom_point() +
  facet_grid(. ~ Expt) +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.1,0.1,0.1,1,0.1,1,0.1,0.1), guide = F) +
  theme_AGL +
  labs(y = "Plot Height", x = "Plot Area")
mp4 <- ggplot(xx, aes(x = Area, y = Height, color = Cluster, alpha = Cluster)) +
  geom_point() +
  facet_grid(. ~ Expt) +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.1,0.1,1,0.1,1,0.1,0.1,0.1), guide = F) +
  theme_AGL +
  labs(y = "Plot Height", x = "Plot Area")
mp <- ggarrange(mp1, mp2, mp3, mp4, ncol = 2, nrow = 2, 
                common.legend = T, legend = "bottom")
ggsave("Figure_101.png", mp, width = 8, height = 6, dpi = 600)
```



```{r echo = F, eval = F}
#
myTi <- myTraits[grepl("GDD", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTi, threshold = 6.7, sug.threshold = 5.3,
                      hlines = c(13.5),
                      vlines = myMarkers, vline.colors = myMColors, vline.legend = F)
ggsave("Additional/GWAS_Summary_5.1_GDD.png", mp, 
       width = 15, height = 8, dpi = 600)
gg_GWAS_plotly(mp, filename = "Additional/pGWAS_Summary_5.1_GDD.html")
#
myTi <- myTraits[grepl("PPD", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTi, threshold = 6.7, sug.threshold = 5.3,
                      hlines = c(13.5),
                      vlines = myMarkers, vline.colors = myMColors, vline.legend = F)
ggsave("Additional/GWAS_Summary_5.2_PPD.png", mp, 
       width = 15, height = 8, dpi = 600)
gg_GWAS_plotly(mp, filename = "Additional/pGWAS_Summary_5.2_PPD.html")
#
myTi <- myTraits[grepl("PTT", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTi, threshold = 6.7, sug.threshold = 5.3,
                      hlines = c(13.5),
                      vlines = myMarkers, vline.colors = myMColors, vline.legend = F)
ggsave("Additional/GWAS_Summary_5.3_PTT.png", mp, 
       width = 15, height = 8, dpi = 600)
gg_GWAS_plotly(mp, filename = "Additional/pGWAS_Summary_5.3_PTT.html")
```


### Presentation Figures

```{r eval = F}
#################################################
# Pres
#################################################
myMColors <- c("red","red","red","red","red",
               "red","red","red","red","red", "red")
myMarkers <- c("Lcu.2RBY.Chr1p356806640", "Lcu.2RBY.Chr1p523664179", "Lcu.2RBY.Chr2p9931198", #"Lcu.2RBY.Chr2p114780722","Lcu.2RBY.Chr3p256160240",
               "Lcu.2RBY.Chr3p142701618", "Lcu.2RBY.Chr3p284827215", "Lcu.2RBY.Chr3p390627702", 
               "Lcu.2RBY.Chr4p2480676", "Lcu.2RBY.Chr4p469781233", 
               "Lcu.2RBY.Chr5p1077484", "Lcu.2RBY.Chr6p267270582", "Lcu.2RBY.Chr6p398156059")# "Lcu.2RBY.Chr6p275594926")
myTs <- myTraits[grepl("Canopy.Height|Plant.Length", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = 10.5,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_01.png", mp, width = 12, height = 6)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_01.html")
#
myMColors <- c("red","red","red","red","red",
               "red","red","red","red","red", "red")
myMarkers <- c("Lcu.2RBY.Chr1p356806640", "Lcu.2RBY.Chr1p523664179", "Lcu.2RBY.Chr2p9931198", #"Lcu.2RBY.Chr2p114780722","Lcu.2RBY.Chr3p256160240",
               "Lcu.2RBY.Chr3p142701618", "Lcu.2RBY.Chr3p284827215", "Lcu.2RBY.Chr3p390627702", 
               "Lcu.2RBY.Chr4p2480676", "Lcu.2RBY.Chr4p469781233", 
               "Lcu.2RBY.Chr5p1077484", "Lcu.2RBY.Chr6p267270582", "Lcu.2RBY.Chr6p398156059")# "Lcu.2RBY.Chr6p275594926")
myTs <- myTraits[grepl("Canopy.Height|Plant.Length", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = 10.5,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_01.png", mp, width = 12, height = 6)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_01.html")
#
myTs <- myTraits[grepl("GrowthRadar", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = 6.5,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_02.png", mp, width = 12, height = 3.5)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_02.html")
#
myTs <- myTraits[grepl("GM", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = 10.5,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_03.png", mp, width = 12, height = 5)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_03.html")
#
myTs <- myTraits[grepl("Biomass|Plant.Mass", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = 15.5,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_04.png", mp, width = 12, height = 6.5)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_04.html")
#
myTs <- myTraits[grepl("Yield|Seed.Mass", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = c(3.5, 6.5),
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_05.png", mp, width = 12, height = 5)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_05.html")
#
myTs <- myTraits[grepl("Width|Branch|Lowest|Node", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = c(3.5, 6.5),
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_06.png", mp, width = 12, height = 6)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_06.html")
#
myTs <- myTraits[grepl("Plot.Height", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = NULL,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_07.png", mp, width = 12, height = 8)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_07.html")
#
myTs <- myTraits[grepl("Volume", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = NULL,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_08.png", mp, width = 12, height = 8)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_08.html")
#
myTs <- myTraits[grepl("Area", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = NULL,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_09.png", mp, width = 12, height = 8)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_09.html")
#
myTs <- myTraits[grepl("gc.v", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = NULL,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_10.png", mp, width = 12, height = 8)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_10.html")
#
myTs <- myTraits[grepl("gc.h", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = NULL,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_11.png", mp, width = 12, height = 8)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_11.html")
#
myTs <- myTraits[grepl("gc.a", myTraits)]
mp <- gg_GWAS_Summary(folder = "GWAS_Results/", traits = myTs, threshold = 6.7, sug.threshold = NULL,
                      hlines = NULL,
                      vlines = myMarkers, vline.colors = myMColors)
ggsave("Additional/GWAS_Summary_mypres_12.png", mp, width = 12, height = 8)
gg_GWAS_plotly(mp, "Additional/GWAS_Summary_mypres_12.html")
```


---

# Additional Figures - Clusters Test

```{r eval = F}
library(factoextra)
library(NbClust)
fviz_nbclust(myPCAinput, kmeans, method = "silhouette")
fviz_nbclust(myPCAinput, kmeans, method = "wss")
fviz_nbclust(myPCAinput, kmeans, method = "gap_stat")
fviz_nbclust(myPCAinput, FUNcluster, method = c("silhouette", "wss", "gap_stat"))
NbClust(data = myPCAinput, diss = NULL, distance = "euclidean",
        min.nc = 2, max.nc = 15, method = "average")
mypca[[3]]
str(mypca)

plot.HCPC(mypcaH,choice='map',draw.tree=FALSE,title='Factor map')
plot.HCPC(mypcaH,choice='3D.map',ind.names=FALSE,centers.plot=FALSE,angle=60,title='Hierarchical tree on the factor map')
png("test.png", width = 1800, height = 1800)
plot.HCPC(mypcaH,choice='tree',title='Hierarchical tree')
dev.off()
mypcaH[[5]]
#
#
#
var <- get_pca_var(mypca)
# Contributions of variables to PC1
mp1 <- fviz_contrib(mypca, choice = "var", axes = 1, top = 15)
# Contributions of variables to PC2
mp2 <- fviz_contrib(mypca, choice = "var", axes = 2, top = 15)
mp3 <- fviz_contrib(mypca, choice = "var", axes = 3, top = 15)
mp <- ggarrange(mp1, mp2, mp3, ncol = 1, nrow = 3)
ggsave("Supplemental_Figure_13.png", mp, width = 6, height = 8, dpi = 600)
# Control variable colors using their contributions to the principle axis
fviz_pca_var(mypca, col.var="contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE # Avoid text overlapping
             ) + theme_minimal() + ggtitle("Variables - PCA")
```

```{r eval = F}
x1 <- it17_gc.v[[2]] %>% select(Expt, Entry, Name, x.min)# %>%
x2 <- su17_gc.v[[2]] %>% select(Expt, Entry, Name, x.min)
xx <- bind_rows(x1,x2) %>% group_by(Expt, Entry, Name)%>%
  summarise(x.min = mean(x.min)) %>%
  left_join(select(myPCA, Name, Cluster), by = "Name")
ggplot(xx, aes(x = Cluster, y = x.min)) +
  geom_quasirandom() +
  facet_grid(Expt~., scales = "free_y") + 
  theme_AGL
```

---

---

# test

myMarkers
myMarkersh
myMarkersa
myMarkersv
myMarkersy
myMarkersp
myMarkersh2
myMarkersa2



```{r}
#
mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf=it17_f, 
                  markers1 = c("Lcu.2RBY.Chr1p382800064","Lcu.2RBY.Chr2p12871875"),
                  #"Lcu.2RBY.Chr1p2011396","Lcu.2RBY.Chr2p12871875" 
                  markers2 = myMarkersd, mypchs = c(2,6,15:18),
                  colors = c("darkred", "darkgreen", "darkgoldenrod3",
                             "darkblue",  "steelblue4", "purple4") )
ggsave("additional/Markers/13_It_3.png", mp,
         width = 9, height = 4, dpi = 600, bg = "white")
mp <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf=su17_f, 
                  markers1 = c("Lcu.2RBY.Chr1p2011396","Lcu.2RBY.Chr2p12871875"), 
                  markers2 = myMarkersd, mypchs = c(2,6,15:18),
                  colors = c("darkred", "darkgreen", "darkgoldenrod3",
                             "darkblue",  "steelblue4", "purple4") )
ggsave("additional/Markers/13_It_4.png", mp,
         width = 9, height = 4, dpi = 600, bg = "white")
#
i <- "Lcu.2RBY.Chr1p2011396"
for(i in c(myMarkersh,myMarkersa,myMarkersv,myMarkersh2,myMarkersa2,myMarkersy) ) {
  mp <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf=su17_f, 
                    markers1 = i, markers2 = myMarkersd)
  ggsave(paste0("additional/Markers/11_Sut_",i,".png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
}
for(i in c(myMarkersh,myMarkersa,myMarkersv,myMarkersh2,myMarkersa2,myMarkersy)) {
  mp <- gg_HAMarker(xh=it17_gc.h, xa=it17_gc.a, xf = it17_f, 
                    markers1 = i, markers2 = myMarkersd)
  ggsave(paste0("additional/Markers/12_Italy_",i,".png"), mp,
         width = 9, height = 4, dpi = 600, bg = "white")
}
#
mp <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf=su17_f, 
                  markers1 = c("Lcu.2RBY.Chr3p286749559", 
                               "Lcu.2RBY.Chr2p12871875",
                               "Lcu.2RBY.Chr1p382800064"
                               ),
                  #, , "Lcu.2RBY.Chr4p6307024","Lcu.2RBY.Chr2p9922218"
                  #"Lcu.2RBY.Chr1p323346547"
                  markers2 = myMarkersd, mypchs = c(2,6,15:18,15:18))
ggsave("additional/Markers/13_Sut_1.png", mp,
         width = 9, height = 4, dpi = 600, bg = "white")
mp <- gg_HAMarker(xh=su17_gc.h, xa=su17_gc.a, xf=su17_f, 
                  markers1 = c("Lcu.2RBY.Chr5p21201394", 
                               "Lcu.2RBY.Chr5p474162648"
                               ),
                  markers2 = myMarkersd, mypchs = c(2,6,15:18))
ggsave("additional/Markers/13_Sut_2.png", mp,
         width = 9, height = 4, dpi = 600, bg = "white")
```

```{r}
marker <- myMarkers[1]
marker2 <- myMarkers[2]
gg_ItalyMarker <- function(marker, marker2 = NULL,
                           colors = c("darkgreen", "darkorange", "steelblue", "darkred")) {
  # Prep data
  xv <- it17_gc.v[[2]] %>% group_by(Entry) %>%
    summarise(Volume = mean(k, na.rm = T))
  xh <- it17_gc.h[[2]] %>% group_by(Entry) %>%
    summarise(Height = mean(k, na.rm = T))
  xa <- it17_gc.a[[2]] %>% group_by(Entry) %>%
    summarise(Area = mean(k, na.rm = T))
  xs <- it17_f %>% filter(Trait == "Seed.Mass") %>%
    group_by(Entry) %>% summarise(Yield = mean(Value, na.rm = T))
  x1 <- myG %>% filter(rs == marker)
  myPCA <- read.csv("myPCA.csv") %>%
    mutate(Name = gsub(" ","_",Name),
           Name = gsub("-","\\.",Name),
           Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
    mutate(Cluster = factor(Cluster))
  if(!is.null(marker2)) {
    x2 <- myG %>% filter(rs == marker2) %>% 
      gather(Name, Allele2, 12:ncol(.)) %>% 
      select(Name, Allele2)
  }
  fname <- paste(marker, marker2, "png", sep = ".")
  title <- paste(marker, marker2, sep = " | ")
  xx <- x1 %>% gather(Name, Allele, 12:ncol(.)) %>%
    select(Name, Allele) %>% 
    filter(Allele %in% c("A", "G","C", "T"))
  if (!is.null(marker2)) { 
    xx <- xx %>% left_join(x2, by = "Name") %>% 
      filter(Allele2 %in% c("A", "G","C", "T")) %>%
      mutate(Allele = paste(Allele, Allele2, sep = "-"))
  }
  xx <- xx %>%
    left_join(select(myPCA, Name, Entry, Cluster, Origin), by = "Name") %>%
    left_join(xv, by = "Entry") %>% 
    left_join(xh, by = "Entry") %>% 
    left_join(xa, by = "Entry") %>% 
    left_join(xs, by = "Entry")
  mp1 <- ggplot(xx, aes(x = Area, y = Height)) + 
    geom_point(aes(color = Allele), alpha = 0.6) + 
    scale_color_manual(name = NULL, values = colors) + 
    theme_AGL #+
    #labs(title = title)
  mp2 <- ggplot(xx, aes(x = Allele, y = Yield)) + 
    geom_quasirandom(aes(color = Allele), alpha = 0.6) + 
    scale_color_manual(name = NULL, values = colors) + 
    theme_AGL +
    labs(caption = title)
  mp <- ggarrange(mp1, mp2, ncol = 2, nrow = 1, common.legend = T)
}
for(i in c(myMarkers,myMarkersh2,myMarkersa2, myMarkersy)) {
  mp <- gg_ItalyMarker(i)
  ggsave(paste0("additional/Markers/09_Italy_",i,".png"), mp,
         width = 9, height = 4, dpi = 600)
}
for(i in myMarkers) {
  mp <- gg_ItalyMarker(myMarkersy[8], i)
  ggsave(paste0("additional/Markers/10_Italy_",i,".png"), mp,
         width = 9, height = 4, dpi = 600)
}
for(i in myMarkers) {
  mp <- gg_ItalyMarker(myMarkersy[8], i)
  ggsave(paste0("additional/Markers/11_Italy_",i,".png"), mp,
         width = 6, height = 4, dpi = 600)
}
gg_ItalyMarker(myMarkers[7], myMarkersy[5])
```



note: need to create a gwas marker plot function

```{r}
# trait <- "Ro17_Yield"; marker <- myMarkersy[1]; marker2 <- myMarkersy[3]; marker2 <- NULL
gg_PlotMarker <- function(myG, myY, trait, marker, marker2 = NULL,
                          colors = c("darkgreen", "darkorange", "steelblue", "darkred")) {
  #
  gwaspr_dna <- data.frame(stringsAsFactors = F, 
    Symbol = c("A", "C", "G", "T", "U", "R", "Y", "S", "W", "K", "M", "N"), 
    Value = c("AA","CC","GG","TT","UU","AG","CT","GC","AT","GT","AC","NN"))
  x1 <- myG %>% filter(rs == marker)
  myPCA <- read.csv("myPCA.csv") %>%
    mutate(Name = gsub(" ","_",Name),
           Name = gsub("-","\\.",Name),
           Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
    mutate(Cluster = factor(Cluster))
  if(!is.null(marker2)) {
    x2 <- myG %>% filter(rs == marker2) %>% 
      gather(Name, Allele2, 12:ncol(.)) %>% 
      select(Name, Allele2)
  }
  fname <- paste(trait, marker, marker2, "png", sep = ".")
  title <- paste(trait, marker, marker2, sep = " | ")
  xx <- x1 %>% gather(Name, Allele, 12:ncol(.)) %>%
    select(Name, Allele) %>% 
    mutate(Allele = plyr::mapvalues(Allele, gwaspr_dna$Symbol, gwaspr_dna$Value), 
           Allele = factor(Allele, levels = gwaspr_dna$Value)) %>% 
    filter(!Allele %in% c("AG","CT","GC","AT","GT","AC","NN"))
  if (!is.null(marker2)) { xx <- xx %>% left_join(x2, by = "Name") }
  xx <- xx %>%
    left_join(select(myPCA, Name, Cluster)) %>%
    left_join(myY, by = "Name") %>% 
    filter(!is.na(get(trait))) %>% 
    mutate(Allele = plyr::mapvalues(Allele, gwaspr_dna$Symbol, gwaspr_dna$Value))
  if(is.null(marker2)) {
    mp <- ggplot(xx, aes(x = Allele, y = get(trait))) + 
      #geom_violin(fill = "grey90") + 
      geom_beeswarm(aes(color = Cluster), cex = 2.5, alpha = 0.6) + 
      geom_boxplot(fill = alpha("white",0), color = alpha("black",0.8),
                   lwd = 1, width = 0.2, outlier.shape = NA, coef = 0) + 
      facet_grid(. ~ as.character(trait)) +
      scale_color_manual(name = NULL, values = myColors_Cluster) + 
      theme_AGL +
      guides(colour = guide_legend(nrow = 1)) +
      #theme(legend.position = "none") +
      labs(y = NULL, x = NULL) #title = title
  } else {
    xx <- xx %>% 
      mutate(Allele2 = plyr::mapvalues(Allele2, gwaspr_dna$Symbol, gwaspr_dna$Value)) %>%
      filter(!Allele2 %in% c("AG","CT","GC","AT","GT","AC","NN")) %>%
      mutate(Allele3 = paste(Allele, Allele2, sep = "-"))
    morder <- xx %>% group_by(Allele3) %>% summarise(Value = mean(get(trait))) %>%
      arrange(Value) %>% pull(Allele3)
    xx <- xx %>% mutate(Allele3 = factor(Allele3, levels = morder))
    mp <- ggplot(xx, aes(x = Allele3, y = get(trait))) + 
      #geom_violin(fill = "grey70") + 
      geom_beeswarm(aes(color = Cluster), cex = 2, alpha = 0.6) + 
      geom_boxplot(fill = alpha("white",0), color = alpha("black",0.8),
                   lwd = 1, width = 0.2, outlier.shape = NA, coef = 0) + 
      facet_grid(. ~ as.character(trait)) +
      scale_color_manual(name = NULL, values = myColors_Cluster) + 
      theme_AGL +
      guides(colour = guide_legend(nrow = 1)) +
      labs(y = NULL, x = NULL)
  }
  mp
}
```


# test markers


```{r}
xx <- read.csv("GWAS_Results_Table.csv") %>%
  filter(Model != "MLMM")
myG <- read.csv("myG_LDP.csv", header = T)
myY <- left_join(
  read.csv("Data_GWAS/myY_it17_gc.csv") %>%
    mutate(Name = gsub(" ","_",Name),
           Name = gsub("-","\\.",Name),
           Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
    as.data.frame() %>%
    select(Name, It17_gc.h.k, It17_gc.a.k, It17_gc.v.k),
  read.csv("Data_GWAS/myY_ro17_gc.csv") %>%
    mutate(Name = gsub(" ","_",Name),
           Name = gsub("-","\\.",Name),
           Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
    as.data.frame() %>%
    select(Name, Ro17_gc.h.k, Ro17_gc.a.k, Ro17_gc.v.k), by = "Name") %>%
  left_join(
    read.csv("Data_GWAS/myY_su17_gc.csv") %>%
      mutate(Name = gsub(" ","_",Name),
             Name = gsub("-","\\.",Name),
             Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
      as.data.frame() %>%
      select(Name, Su17_gc.h.k, Su17_gc.a.k, Su17_gc.v.k), by = "Name") %>%
  left_join(
    read.csv("Data_GWAS/myY_myF.csv") %>%
      mutate(Name = gsub(" ","_",Name),
             Name = gsub("-","\\.",Name),
             Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
      as.data.frame() %>%
      select(Name, contains("Yield")), by = "Name")
#
i<-myMarkers[1]
for(i in myMarkersd) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/01_DTF_",i,".png"), mp, 
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersh) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/02_Height_",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersa) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/03_Area_",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersv) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/04_Volume_",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersh2) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/05_Height_",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersa2) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/06_Area_",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersp) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/07_PCA_",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
#
for(i in myMarkersy) {
  mp1 <- gg_PlotMarker(myG, myY, "In16_Yield", i)
  mp2 <- gg_PlotMarker(myG, myY, "In17_Yield", i)
  mp3 <- gg_PlotMarker(myG, myY, "Ba16_Yield", i)
  mp4 <- gg_PlotMarker(myG, myY, "Ba17_Yield", i)
  mp5 <- gg_PlotMarker(myG, myY, "Ne16_Yield", i)
  mp6 <- gg_PlotMarker(myG, myY, "Ne17_Yield", i)
  mp7 <- gg_PlotMarker(myG, myY, "Mo16_Yield", i)
  mp8 <- gg_PlotMarker(myG, myY, "Mo17_Yield", i)
  mp9 <- gg_PlotMarker(myG, myY, "Sp16_Yield", i)
  mp10 <- gg_PlotMarker(myG, myY, "Sp17_Yield", i)
  mp11 <- gg_PlotMarker(myG, myY, "It16_Yield", i)
  mp12 <- gg_PlotMarker(myG, myY, "It17_Yield", i)
  mp13 <- gg_PlotMarker(myG, myY, "Ro16_Yield", i)
  mp14 <- gg_PlotMarker(myG, myY, "Ro17_Yield", i)
  mp15 <- gg_PlotMarker(myG, myY, "Su16_Yield", i)
  mp16 <- gg_PlotMarker(myG, myY, "Su17_Yield", i)
  mp17 <- gg_PlotMarker(myG, myY, "Su18_Yield", i)
  mp18 <- gg_PlotMarker(myG, myY, "Us18_Yield", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  mp10, mp11, mp12, mp13, mp14, mp15, mp16, mp17, mp18,
                  ncol = 6, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/08_Yield_",i,".png"), mp, 
         width = 12, height = 8, dpi = 600, bg = "white")
}
#gg_Marker(myG, myY, "Su17_gc.h.k", "Lcu.2RBY.Chr1p523664179", type = "box")
#
```





```{r}
xi <- xx %>% 
  filter(X.log10.p. > 7, Model != "MLMM") %>% 
  filter(!duplicated(SNP)) %>%
  mutate(HBP_log = -log10(H.B.P.Value)) %>% 
  filter(HBP_log > 6.7)
for(i in xi$SNP) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", i)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", i)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", i)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", i)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", i)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", i)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", i)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", i)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", i)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/MarkersAll/",i,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
```




```{r}
# Figure 6
myMarkersa
myMarkersh
myMarkersv
#
m1<-"Lcu.2RBY.Chr1p384688046"
m2<-"Lcu.2RBY.Chr7p528136791"
gg_DoubleMarkerPlot <- function(myG, myY, m1, m2) {
  mp1 <- gg_PlotMarker(myG, myY, "It17_gc.h.k", m1, m2)
  mp2 <- gg_PlotMarker(myG, myY, "It17_gc.a.k", m1, m2)
  mp3 <- gg_PlotMarker(myG, myY, "It17_gc.v.k", m1, m2)
  mp4 <- gg_PlotMarker(myG, myY, "Su17_gc.h.k", m1, m2)
  mp5 <- gg_PlotMarker(myG, myY, "Su17_gc.a.k", m1, m2)
  mp6 <- gg_PlotMarker(myG, myY, "Su17_gc.v.k", m1, m2)
  mp7 <- gg_PlotMarker(myG, myY, "Ro17_gc.h.k", m1, m2)
  mp8 <- gg_PlotMarker(myG, myY, "Ro17_gc.a.k", m1, m2)
  mp9 <- gg_PlotMarker(myG, myY, "Ro17_gc.v.k", m1, m2)
  mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                  ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
  ggsave(paste0("additional/Markers/Double_",m1,"_",m2,".png"), mp,
         width = 12, height = 8, dpi = 600, bg = "white")
}
# ggsave(paste0("additional/MarkersAll/",i,".png"), mp,
#          width = 12, height = 8, dpi = 600, bg = "white")
#
# Area
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p234027120", m2 = "Lcu.2RBY.Chr2p136778592")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p384688046", m2 = "Lcu.2RBY.Chr7p528136791") # small vol italy
# Height
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr7p26181956", m2 = "Lcu.2RBY.Chr2p68928307")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p2011396", m2 = "Lcu.2RBY.Chr7p26181956")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p2011396", m2 = "Lcu.2RBY.Chr2p68928307")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p2011396", m2 = "Lcu.2RBY.Chr1p523664179")
#
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p14219576", m2 = "Lcu.2RBY.Chr1p2011396")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p14219576", m2 = "Lcu.2RBY.Chr4p477030581")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p14219576", m2 = "Lcu.2RBY.Chr5p444371450")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p14219576", m2 = "Lcu.2RBY.Chr1p523664179")
# half/half
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p2011396", m2 = "Lcu.2RBY.Chr2p136778592")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr5p444371450", m2 = "Lcu.2RBY.Chr4p477030581")
# select high
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p68928307", m2 = "Lcu.2RBY.Chr2p14219576") # high both
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr2p68928307", m2 = "Lcu.2RBY.Chr1p384688046")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p2011396", m2 = "Lcu.2RBY.Chr1p384688046")
gg_DoubleMarkerPlot(myG, myY, m1 = "Lcu.2RBY.Chr1p2011396", m2 = "Lcu.2RBY.Chr2p14219576")
```


## multimarkers

```{r}
trait <- "It17_gc.v.k"
markers <- myMarkersp
gg_MultiMarker <- function(myG, myY, trait, markers, 
                           m_levels = NULL) {
  #
  gwaspr_dna <- data.frame(stringsAsFactors = F, 
    Symbol = c("A", "C", "G", "T", "U", "R", "Y", "S", "W", "K", "M", "N"), 
    Value = c("AA","CC","GG","TT","UU","AG","CT","GC","AT","GT","AC","NN"))
  x1 <- myG %>% filter(rs %in% markers)
  myPCA <- read.csv("myPCA.csv") %>%
    mutate(Name = gsub(" ","_",Name),
           Name = gsub("-","\\.",Name),
           Name = plyr::mapvalues(Name, "3156.11_AGL", "X3156.11_AGL")) %>%
    mutate(Cluster = factor(Cluster))
  #
  #fname <- paste(trait, marker, marker2, "png", sep = ".")
  #title <- paste(trait, marker, marker2, sep = " | ")
  xx <- x1 %>% select(-2,-3,-4,-5,-6,-7,-8,-9,-10,-11) %>% t() %>%
    as.data.frame() %>% slice(-1) %>%
    mutate(Markers = "")
  j <- ncol(xx)
  for(i in 1:(length(xx)-1)) { xx[,j] <- paste0(xx[,j], xx[,i]) }
  xx <- xx %>% filter(!grepl("U|R|Y|S|W|K|M|N", Markers)) %>%
    rownames_to_column("Name") %>%
    select(Name, Markers)
  #
  xx <- xx %>%
    left_join(select(myPCA, Name, Cluster, Origin), by = "Name") %>%
    left_join(myY, by = "Name") %>% 
    filter(!is.na(get(trait)))
  yy <- xx %>% group_by(Markers) %>% 
    summarise(Avg = mean(get(trait), na.rm = T), Count = n()) %>%
    arrange(Avg) %>% filter(Count > 11)
  if(is.null(m_levels)) { 
    xx <- xx %>% mutate(Markers = factor(Markers, levels = yy$Markers)) %>%
      filter(!is.na(Markers))
  } else { xx <- xx %>% mutate(Markers = factor(Markers, levels = m_levels)) %>%
      filter(!is.na(Markers))}
    #mutate(Allele = plyr::mapvalues(Allele, gwaspr_dna$Symbol, gwaspr_dna$Value))
  xx <- xx %>% mutate(Origin2 = ifelse(Origin == "Canada", "Canada", "Other"))
  #
  mp <- ggplot(xx, aes(x = Markers, y = get(trait))) + 
    geom_beeswarm(aes(fill = Cluster, color = Origin2), pch = 21, cex = 1.5, alpha = 0.6) + 
    geom_boxplot(fill = alpha("white",0), color = alpha("black",0.4),
                 lwd = 1, width = 0.2, outlier.shape = NA, coef = 0) + 
    facet_grid(. ~ as.character(trait)) +
    scale_fill_manual(name = NULL, values = myColors_Cluster) + 
    scale_color_manual(name = "Origin", values = c("black", "white")) +
    theme_AGL +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    guides(colour = guide_legend(nrow = 1)) +
    #theme(legend.position = "none") +
    labs(y = NULL, x = NULL) #title = title
  mp
}
```

```{r}
# Prep data
myMarkers_su <- c("Lcu.2RBY.Chr1p2011396", "Lcu.2RBY.Chr1p381072414", 
                "Lcu.2RBY.Chr1p323346547", "Lcu.2RBY.Chr4p6307024")
# Plot
i <- myMarkers_su
mp1 <- gg_MultiMarker(myG, myY, "It17_gc.h.k", markers = i)
mp2 <- gg_MultiMarker(myG, myY, "It17_gc.a.k", i)
mp3 <- gg_MultiMarker(myG, myY, "It17_gc.v.k", i)
mp4 <- gg_MultiMarker(myG, myY, "Su17_gc.h.k", i)
mp5 <- gg_MultiMarker(myG, myY, "Su17_gc.a.k", i)
mp6 <- gg_MultiMarker(myG, myY, "Su17_gc.v.k", i)
mp7 <- gg_MultiMarker(myG, myY, "Ro17_gc.h.k", i)
mp8 <- gg_MultiMarker(myG, myY, "Ro17_gc.a.k", i)
mp9 <- gg_MultiMarker(myG, myY, "Ro17_gc.v.k", i)
mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
ggsave(paste0("additional/Markers/00_Su.png"), mp,
       width = 12, height = 8, dpi = 600, bg = "white")
#
my_m_levels <- c("ACCA","GCTA","AACA","AATA",
                 "GACA","GATA","GACG","GATG")
mp1 <- gg_MultiMarker(myG, myY, "It17_gc.v.k", markers = i, m_levels=my_m_levels)
mp2 <- gg_MultiMarker(myG, myY, "Su17_gc.v.k", i, my_m_levels)
mp3 <- gg_MultiMarker(myG, myY, "Ro17_gc.v.k", i, my_m_levels)
mp <- ggarrange(mp1, mp2, mp3, ncol = 1, nrow = 3, 
                common.legend = T, legend = "bottom")
ggsave(paste0("additional/Markers/00_Su2.png"), mp,
       width = 4, height = 8, dpi = 600, bg = "white")
#
myMarkers_su <- c(#"Lcu.2RBY.Chr1p2011396", "Lcu.2RBY.Chr1p381072414", 
                "Lcu.2RBY.Chr1p323346547", "Lcu.2RBY.Chr4p6307024", 
                "Lcu.2RBY.Chr7p528136791", "Lcu.2RBY.Chr5p458058460")
# Plot
i <- myMarkers_su
mp1 <- gg_MultiMarker(myG, myY, "It17_gc.h.k", markers = i)
mp2 <- gg_MultiMarker(myG, myY, "It17_gc.a.k", i)
mp3 <- gg_MultiMarker(myG, myY, "It17_gc.v.k", i)
mp4 <- gg_MultiMarker(myG, myY, "Su17_gc.h.k", i)
mp5 <- gg_MultiMarker(myG, myY, "Su17_gc.a.k", i)
mp6 <- gg_MultiMarker(myG, myY, "Su17_gc.v.k", i)
mp7 <- gg_MultiMarker(myG, myY, "Ro17_gc.h.k", i)
mp8 <- gg_MultiMarker(myG, myY, "Ro17_gc.a.k", i)
mp9 <- gg_MultiMarker(myG, myY, "Ro17_gc.v.k", i)
mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
ggsave(paste0("additional/Markers/00_Su3.png"), mp,
       width = 12, height = 8, dpi = 600, bg = "white")
```

```{r}
#
i <- myMarkersp
mp1 <- gg_MultiMarker(myG, myY, "It17_gc.h.k", i)
mp2 <- gg_MultiMarker(myG, myY, "It17_gc.a.k", i)
mp3 <- gg_MultiMarker(myG, myY, "It17_gc.v.k", i)
mp4 <- gg_MultiMarker(myG, myY, "Su17_gc.h.k", i)
mp5 <- gg_MultiMarker(myG, myY, "Su17_gc.a.k", i)
mp6 <- gg_MultiMarker(myG, myY, "Su17_gc.v.k", i)
mp7 <- gg_MultiMarker(myG, myY, "Ro17_gc.h.k", i)
mp8 <- gg_MultiMarker(myG, myY, "Ro17_gc.a.k", i)
mp9 <- gg_MultiMarker(myG, myY, "Ro17_gc.v.k", i)
mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
ggsave(paste0("additional/Markers/All_PCA.png"), mp,
       width = 12, height = 8, dpi = 600, bg = "white")
#
i <- c(myMarkersa[1], myMarkersa[5], myMarkersh[1])#, myMarkersh[3])#, myMarkersp[3])#,
#i <- c(myMarkersv[5:7])#, myMarkersv[1:2])
mp1 <- gg_MultiMarker(myG, myY, "It17_gc.h.k", i)
mp2 <- gg_MultiMarker(myG, myY, "It17_gc.a.k", i)
mp3 <- gg_MultiMarker(myG, myY, "It17_gc.v.k", i)
mp4 <- gg_MultiMarker(myG, myY, "Su17_gc.h.k", i)
mp5 <- gg_MultiMarker(myG, myY, "Su17_gc.a.k", i)
mp6 <- gg_MultiMarker(myG, myY, "Su17_gc.v.k", i)
mp7 <- gg_MultiMarker(myG, myY, "Ro17_gc.h.k", i)
mp8 <- gg_MultiMarker(myG, myY, "Ro17_gc.a.k", i)
mp9 <- gg_MultiMarker(myG, myY, "Ro17_gc.v.k", i)
mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
ggsave(paste0("additional/Markers/All_triple.png"), mp,
       width = 12, height = 8, dpi = 600, bg = "white")
#
i <- c(myMarkersh[1], myMarkersa[1], myMarkersv[4])#, myMarkersh[3])#, myMarkersp[3])#,
#i <- c(myMarkersv[5:7])#, myMarkersv[1:2])
mp1 <- gg_MultiMarker(myG, myY, "It17_gc.h.k", i)
mp2 <- gg_MultiMarker(myG, myY, "It17_gc.a.k", i)
mp3 <- gg_MultiMarker(myG, myY, "It17_gc.v.k", i)
mp4 <- gg_MultiMarker(myG, myY, "Su17_gc.h.k", i)
mp5 <- gg_MultiMarker(myG, myY, "Su17_gc.a.k", i)
mp6 <- gg_MultiMarker(myG, myY, "Su17_gc.v.k", i)
mp7 <- gg_MultiMarker(myG, myY, "Ro17_gc.h.k", i)
mp8 <- gg_MultiMarker(myG, myY, "Ro17_gc.a.k", i)
mp9 <- gg_MultiMarker(myG, myY, "Ro17_gc.v.k", i)
mp <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, 
                ncol = 3, nrow = 3, common.legend = T, legend = "bottom")
ggsave(paste0("additional/Markers/All_triple2.png"), mp,
       width = 12, height = 8, dpi = 600, bg = "white")
#

```

---

## GDD

```{r echo = F, eval = F}
# Drone data Growth Curves
x1 <- it17_gdd.v %>% mutate(Expt = "It17_v")
x2 <- it17_gdd.h %>% mutate(Expt = "It17_h")
x3 <- it17_gdd.a %>% mutate(Expt = "It17_a")
xx <- bind_rows(x1,x2,x3) %>%
  select(Name, Expt, 
         GDD.mid, GDD.mid, GDD.max, GDD.max.DTF, GDD.x.d, 
         PPD.mid, PPD.mid, PPD.max, PPD.max.DTF, PPD.x.d, 
         PTT.mid, PTT.mid, PTT.max, PTT.max.DTF, PTT.x.d ) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Name, Expt, Trait) %>%
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>% mutate(Trait = paste(Expt, Trait, sep = ".")) %>%
  select(-Expt) %>% spread(Trait, Value)
write.csv(xx, "Data_GWAS/myY_it17_gdd.csv", row.names = F)
#
x1 <- ro17_gdd.v %>% mutate(Expt = "Ro17_v")
x2 <- ro17_gdd.h %>% mutate(Expt = "Ro17_h")
x3 <- ro17_gdd.a %>% mutate(Expt = "Ro17_a")
xx <- bind_rows(x1,x2,x3) %>%
  select(Name, Expt, 
         GDD.mid, GDD.mid, GDD.max, GDD.max.DTF, GDD.x.d, 
         PPD.mid, PPD.mid, PPD.max, PPD.max.DTF, PPD.x.d, 
         PTT.mid, PTT.mid, PTT.max, PTT.max.DTF, PTT.x.d ) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Name, Expt, Trait) %>%
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>% mutate(Trait = paste(Expt, Trait, sep = ".")) %>%
  select(-Expt) %>% spread(Trait, Value)
write.csv(xx, "Data_GWAS/myY_ro17_gdd.csv", row.names = F)
#
x1 <- su17_gdd.v %>% mutate(Expt = "Su17_v")
x2 <- su17_gdd.h %>% mutate(Expt = "Su17_h")
x3 <- su17_gdd.a %>% mutate(Expt = "Su17_a")
xx <- bind_rows(x1,x2,x3) %>%
  select(Name, Expt, 
         GDD.mid, GDD.mid, GDD.max, GDD.max.DTF, GDD.x.d, 
         PPD.mid, PPD.mid, PPD.max, PPD.max.DTF, PPD.x.d, 
         PTT.mid, PTT.mid, PTT.max, PTT.max.DTF, PTT.x.d ) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Name, Expt, Trait) %>%
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>% mutate(Trait = paste(Expt, Trait, sep = ".")) %>%
  select(-Expt) %>% spread(Trait, Value)
write.csv(xx, "Data_GWAS/myY_su17_gdd.csv", row.names = F)
```

# Figure 07 - Volume x Seed.Mass

```{r}
# Volume
x1.1 <- rbind(it17_gc.v[[2]], ro17_gc.v[[2]], su17_gc.v[[2]]) %>%
  select(Plot, Name, Expt, Value=k)
x2 <- rbind(it17_f %>% filter(Trait == "Seed.Mass"),
            ro17_f %>% filter(Trait == "Seed.Mass"),
            su17_f %>% filter(Trait == "Seed.Mass") ) %>%
  select(Plot, Name, Expt, Seed.Mass=Value) 
x3 <- read.csv("myPCA.csv") %>%
  mutate(Cluster = factor(Cluster)) %>%
  select(Name, Entry, Cluster)
#
xx1 <- x1.1 %>% 
  left_join(x2, by = c("Plot","Name","Expt")) %>%
  left_join(x3, by = "Name") %>%
  group_by(Entry, Name, Expt, Cluster) %>%
  summarise(Seed.Mass = mean(Seed.Mass, na.rm = T),
            Value = mean(Value, na.rm = T)) %>%
  mutate(Adapted = ifelse(Expt == "Italy 2017" & Seed.Mass > 150, "Adapted", "Unadapted"),
         Adapted = ifelse(Expt == "Sutherland 2017" & Seed.Mass > 300, "Adapted", Adapted),
         Adapted = ifelse(Expt == "Rosthern 2017" & Seed.Mass > 300, "Adapted", Adapted),
         Trait = "Volume")
mp <- ggplot(xx1, aes(x = Value, y = Seed.Mass, 
                     color = Cluster, alpha = Adapted)) +
  geom_point() +
  facet_wrap(Expt ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.7, 0.1)) +
  theme_AGL
#
# Height
#
x1.2 <- rbind(it17_gc.h[[2]], ro17_gc.h[[2]], su17_gc.h[[2]]) %>%
  select(Plot, Name, Expt, Value=k)
#
xx2 <- x1.2 %>% 
  left_join(x2, by = c("Plot","Name","Expt")) %>%
  left_join(x3, by = "Name") %>%
  group_by(Entry, Name, Expt, Cluster) %>%
  summarise(Seed.Mass = mean(Seed.Mass, na.rm = T),
            Value = mean(Value, na.rm = T)) %>%
  mutate(Adapted = ifelse(Expt == "Italy 2017" & Seed.Mass > 150, "Adapted", "Unadapted"),
         Adapted = ifelse(Expt == "Sutherland 2017" & Seed.Mass > 300, "Adapted", Adapted),
         Adapted = ifelse(Expt == "Rosthern 2017" & Seed.Mass > 300, "Adapted", Adapted),
         Trait = "Height")
mp2 <- ggplot(xx2, aes(x = Value, y = Seed.Mass, 
                     color = Cluster, alpha = Adapted)) +
  geom_point() +
  facet_wrap(Expt ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.7, 0.1)) +
  theme_AGL
#
# Area
#
x1.3 <- rbind(it17_gc.a[[2]], ro17_gc.a[[2]], su17_gc.a[[2]]) %>%
  select(Plot, Name, Expt, Value=k)
#
xx3 <- x1.3 %>% 
  left_join(x2, by = c("Plot","Name","Expt")) %>%
  left_join(x3, by = "Name") %>%
  group_by(Entry, Name, Expt, Cluster) %>%
  summarise(Seed.Mass = mean(Seed.Mass, na.rm = T),
            Value = mean(Value, na.rm = T)) %>%
  mutate(Adapted = ifelse(Expt == "Italy 2017" & Seed.Mass > 150, "Adapted", "Unadapted"),
         Adapted = ifelse(Expt == "Sutherland 2017" & Seed.Mass > 300, "Adapted", Adapted),
         Adapted = ifelse(Expt == "Rosthern 2017" & Seed.Mass > 300, "Adapted", Adapted),
         Trait = "Area")
mp3 <- ggplot(xx3, aes(x = Value, y = Seed.Mass, 
                     color = Cluster, alpha = Adapted)) +
  geom_point() +
  facet_wrap(Expt ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.7, 0.1)) +
  theme_AGL
#
xx <- bind_rows(xx1,xx2,xx3)
mp <- ggplot(xx, aes(y = Value, x = Seed.Mass, 
                     color = Cluster, alpha = Adapted)) +
  geom_point() +
  facet_wrap(Expt ~ Trait, scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.7, 0.1)) +
  theme_AGL
ggsave("Figure_23.png", mp, width = 10, height = 8, dpi = 600)
#

```

# Compare PCA clusters

```{r}
x1 <- read.csv("myPCA.csv") %>%
  select(Entry, Name, Growth_Cluster=Cluster) %>% 
  mutate(Growth_Cluster = factor(Growth_Cluster))
#x2 <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_pca_results.csv") %>% 
#  select(Name, DTF_Cluster=Cluster)
x2 <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/dblogr/master/content/academic/lentil_diversity_panel/data_ldp.csv") %>% 
  select(Name, STR_Group)
xx <- left_join(x1, x2, by = "Name")
ggplot(xx, aes(x = Growth_Cluster, y = STR_Group, color = as.factor(Growth_Cluster))) +
  geom_point() +
  scale_color_manual(values = myColors_Cluster)
mp <- ggplot(xx, aes(x = Growth_Cluster)) +
  geom_bar(aes(fill = Growth_Cluster)) +
  facet_grid(. ~ STR_Group) +
  theme_AGL +
  scale_fill_manual(values = myColors_Cluster)
ggsave("Figure_51.png", mp, width = 8, height = 4, dpi = 600)
```


## S Figure 09 - GDD???

```{r}
# xx <- ro17_gc.v[[3]]
ggGDDCurves <- function(xx, myTitle = NULL, plotType = "Entries") {
  #
  myEnvs <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_env.csv") %>%
    rename(DAP=DaysAfterPlanting) %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt))
  myCoefs <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_tb_pc_raw.csv") %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt))
  #
  xx <- xx %>% mutate(Date = as.Date(Planting.Date) + DAP,
                      Date = as.character(Date)) %>%
    left_join(select(myCoefs, Plot, Expt, Tb), by = c("Plot","Expt")) %>% 
    left_join(select(myEnvs, Expt, DAP, Temp_mean), by = c("Expt","DAP")) %>%
    mutate(GDD = Temp_mean - Tb)
  xx <- xx %>% group_by(Plot, Rep, Entry, Name, Expt) %>% arrange(DAP) %>%
    mutate(CGDD = cumsum(GDD)) %>% ungroup() %>% 
    group_by(Entry, Name, Expt, CGDD) %>%
    summarise(Predicted.Values = mean(Predicted.Values, na.rm = T))
  #
  x1 <- xx %>% filter(Entry %in% c(19,94,107,252))
  if(plotType == "Entries") {
    mp <- ggplot(xx, aes(x = CGDD, y = Predicted.Values, group = Name)) +
      geom_line(alpha = 0.1) +
      geom_line(data = x1, aes(color = Name)) +
      #facet_grid(. ~ Rep) +
      theme_AGL +
      theme(legend.position = "bottom") +
      scale_color_manual(name = NULL, 
                         values = c("darkgreen","darkred","darkblue","steelblue")) +
      labs(title = myTitle)
  }
  if(plotType == "PCA") {
    xx <- xx %>% left_join(select(myPCA, Name, Cluster), by = "Name") %>% 
      mutate(Cluster = as.character(Cluster),
             Group = Cluster)
    xx <- xx %>% 
      bind_rows(xx %>% mutate(Group = "1", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "2", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "3", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "4", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "5", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "6", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "7", Cluster = "0")) %>%
      bind_rows(xx %>% mutate(Group = "8", Cluster = "0")) %>%
      arrange(Cluster)
    mp <- ggplot(xx, aes(x = CGDD, y = Predicted.Values, group = Name, color = Cluster)) +
      geom_line() +
      #geom_line(data = x1, aes(color = Name)) +
      facet_wrap(Group ~ ., ncol = 4) +
      scale_color_manual(values = c(alpha("Black",0.1), myColors_Cluster)) +
      theme_AGL +
      labs(title = myTitle)
  }
  mp
}
#mp1 <- ggGDDCurves(xx = it17_gc.v[[3]], myTitle = "Italy 2017")
#mp2 <- ggGDDCurves(xx = ro17_gc.v[[3]], myTitle = "Rosthern 2017")
#mp3 <- ggGDDCurves(xx = su17_gc.v[[3]], myTitle = "Sutherland 2017")
#mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
#ggsave("Additional/ggGDDCurves_Volume.png", mp, width = 10, height = 4)
#
#mp1 <- ggGDDCurves(xx = it17_gc.v[[3]], myTitle = "Italy 2017 Volume")
#mp2 <- ggGDDCurves(xx = it17_gc.h[[3]], myTitle = "Height")
#mp3 <- ggGDDCurves(xx = it17_gc.a[[3]], myTitle = "Area")
#mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
#ggsave("Additional/ggGDDCurves_VHA_It17.png", mp, width = 10, height = 4)
#
#mp1 <- ggGDDCurves(xx = ro17_gc.v[[3]], myTitle = "Rosthern 2017 Volume")
#mp2 <- ggGDDCurves(xx = ro17_gc.h[[3]], myTitle = "Height")
#mp3 <- ggGDDCurves(xx = ro17_gc.a[[3]], myTitle = "Area")
#mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
#ggsave("Additional/ggGDDCurves_VHA_Ro17.png", mp, width = 10, height = 4)
#
#mp1 <- ggGDDCurves(xx = su17_gc.v[[3]], myTitle = "Sutherland 2017 Volume")
#mp2 <- ggGDDCurves(xx = su17_gc.h[[3]], myTitle = "Height")
#mp3 <- ggGDDCurves(xx = su17_gc.a[[3]], myTitle = "Area")
#mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
#ggsave("Additional/ggGDDCurves_VHA_Su17.png", mp, width = 10, height = 4)
#
mp1 <- ggGDDCurves(xx = it17_gc.v[[3]], myTitle = "Italy 2017", plotType = "PCA")
ggsave("Supplemental_Figure_09_1.png", mp1, width = 8, height = 4)
mp2 <- ggGDDCurves(xx = ro17_gc.v[[3]], myTitle = "Rosthern 2017", plotType = "PCA")
ggsave("Supplemental_Figure_09_2.png", mp2, width = 8, height = 4)
#ggsave("Additional/ggGDDCurves_Ro17_PCA_Volume.png", mp, width = 8, height = 6)
mp3 <- ggGDDCurves(xx = su17_gc.v[[3]], myTitle = "Sutherland 2017", plotType = "PCA")
ggsave("Supplemental_Figure_09_3.png", mp3, width = 8, height = 4)
#ggsave("Additional/ggGDDCurves_Su17_PCA_Volume.png", mp, width = 8, height = 6)
mp <- ggarrange(mp1, mp2, mp3, nrow = 3, common.legend = T)
ggsave("Supplemental_Figure_09_4.png", mp, width = 8, height = 12)
```

# DTF

```{r}
# Prep data

```

# HA ratio

```{r}
ggHA3 <- function(xH, xA, xV, xPCA) { #, xlims, ylims
  # Prep data
  xH <- xH %>% select(Plot, Entry, Expt, Height=k)
  xA <- xA %>% select(Plot, Entry, Area=k)
  xV <- xV %>% select(Plot, Entry, Volume=k)
  xPCA <- xPCA %>% select(Entry, Cluster)
  xx <- left_join(xH, xA, by = c("Plot","Entry")) %>%
    left_join(xV, by = c("Plot","Entry")) %>%
    group_by(Entry, Expt) %>%
    summarise(Height = mean(Height, na.rm = T),
              Area = mean(Area, na.rm = T),
              Volume = mean(Volume, na.rm = T)) %>%
    ungroup() %>%
    mutate(HA_ratio = Height / Area) %>%
    left_join(xPCA, by = "Entry")
  # Plot
  ggplot(xx, aes(x = Cluster, y = HA_ratio, color = Cluster), size = Volume) +
    geom_point() +
    facet_grid(. ~ Expt) +
    scale_color_manual(values = myColors_Cluster) +
    scale_size_continuous(range = c(0.25,2.5)) +
    #xlim(xlims) + ylim(ylims) +
    theme_AGL 
}
mp1 <- ggHA3(xH = it17_gc.h[[2]], xA = it17_gc.a[[2]], xV = it17_gc.v[[2]], xPCA=myPCA)
mp2 <- ggHA3(xH = su17_gc.h[[2]], xA = su17_gc.a[[2]], xV = it17_gc.v[[2]], xPCA=myPCA)
mp <- ggarrange(mp1, mp2, ncol = 2, nrow = 1,
                common.legend = T, legend = "right")
mp
ggsave("Figure_55.png", mp, width = 8, height = 4, dpi = 600)
```

# harvest index

```{r}
y1 <- it17_f %>% filter(Trait == "Seed.Mass") %>% select(Plot, Name, Seed.Mass=Value)
y2 <- it17_gc.v[[2]] %>% select(Plot, Volume=k)
x1 <- left_join(y1, y2, by = "Plot") %>%
  mutate(Expt = "Italy 2017",
         Harvest.Index = Seed.Mass / Volume)
#
y1 <- su17_f %>% filter(Trait == "Seed.Mass") %>% select(Plot, Name, Seed.Mass=Value)
y2 <- su17_gc.v[[2]] %>% select(Plot, Volume=k)
x2 <- left_join(y1, y2, by = "Plot") %>%
  mutate(Expt = "Sutherland 2017",
         Harvest.Index = Seed.Mass / Volume)
xx <- bind_rows(x1, x2) %>%
  group_by(Name, Expt) %>%
  summarise(Harvest.Index = mean(Harvest.Index, na.rm = T)) %>%
  left_join(select(myPCA, Name, Cluster), by = "Name") %>%
  left_join(myPCAinput %>% rownames_to_column("Name") %>%
              select(Name, Su17_v.perc.DTF, It17_v.perc.DTF ), by = "Name")
#
ggplot(xx, aes(x = Expt, y = Harvest.Index, color = Cluster)) +
  geom_quasirandom() +
  scale_color_manual(values = myColors_Cluster)
mp1 <- ggplot(xx %>% filter(Expt == "Italy 2017"), 
       aes(x = It17_v.perc.DTF, y = Harvest.Index, color = Cluster)) +
  geom_quasirandom() +
  scale_color_manual(values = myColors_Cluster)
mp2 <- ggplot(xx %>% filter(Expt == "Sutherland 2017"), 
       aes(x = Su17_v.perc.DTF, y = Harvest.Index, color = Cluster)) +
  geom_quasirandom() +
  scale_color_manual(values = myColors_Cluster)
mp <- ggarrange(mp1, mp2, ncol = 2, nrow = 1, common.legend = T, legend = "bottom")
ggsave("Figure_51.png", mp, width = 8, height = 4, dpi = 600)
```


```{r}
x1 <- it17_f %>% filter(Trait == "Canopy.Height")
x2 <- su17_f %>% filter(Trait == "Canopy.Height")
x3 <- it17_gc.h[[2]] %>% filter(Trait == "Canopy.Height")
x4 <- su17_gc.h[[2]] %>% filter(Trait == "Canopy.Height")
xx <- rbind(x1, x2) %>%
  group_by(Entry, Name, Expt, Trait) %>%
  summarise(Value = mean(Value, na.rm = T))
ggplot(xx, aes(x = Expt, y = Value)) +
  geom_quasirandom()
unique(xx$Trait)
```


## odd growth curves

```{r}

ggGrowthCurve <- function(xg, myTrait,
                          myTitle = NULL, #myPrefix, mySuffix, days, 
                          myEntries = c(9, 35, 73, 94, 113),
                          myColors = c("darkgreen", "darkgoldenrod3", "darkred",
                                       "steelblue4", "darkslategray"), linesize = 2 ) {
  #
  xpm <- xg[[3]]
  if(sum(colnames(xpm)=="Expt")==0) { xpm <- xpm %>% mutate(Expt = myTitle) }
  xpe <- xpm %>% filter(Entry %in% myEntries) %>%
    mutate(Entry = factor(Entry, levels = myEntries))
  mp <- ggplot(xpm, aes(x = DAP, y = Predicted.Values, group = Entry, key1 = Name)) +
    geom_line(alpha = 0.05) +
    geom_line(data = xpe, size = linesize, alpha = 0.8,
              aes(color = paste0(Name," (",Entry,")"))) +
    facet_grid(. ~ Expt, scales = "free_x", space = "free_x") +
    scale_color_manual(name = NULL, values = myColors) +
    #theme(legend.position = "bottom") +
    theme_AGL + 
    #guides(color = guide_legend(nrow = 1)) +
    labs(x = "Days After Planting")
  mp
}
xg <- it17_gc.v[[2]] %>% group_by(group) %>% top_n(1, x) 

```


# DTF x Volume

```{r}
x1 <- rbind(it17_f %>% filter(Trait %in% c("DTF", "Seed.Mass")),
            ro17_f %>% filter(Trait %in% c("DTF", "Seed.Mass")),
            su17_f %>% filter(Trait %in% c("DTF", "Seed.Mass"))) %>%
  spread(Trait, Value) %>%
  group_by(Expt) %>%
  mutate(Seed.Mass_scaled = scales::rescale(Seed.Mass))
x2 <- rbind(it17_gc.v[[2]],
            ro17_gc.v[[2]],
            su17_gc.v[[2]]) %>%
  select(Plot, Volume=k)
x3 <- read.csv("myPCA.csv") %>%
  select(Name, Cluster)
xx <- left_join(x1, x2, by = "Plot") %>%
  left_join(x3, by = "Name") %>%
  mutate(Cluster = factor(Cluster))
#
mp1 <- ggplot(xx, aes(x = DTF, y = Volume, color = Cluster)) +
  geom_point(alpha = 0.7) +
  facet_wrap(Expt ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  #scale_size_continuous(range = c(0.25,3)) +
  theme_AGL
mp2 <- ggplot(xx, aes(x = DTF, y = Seed.Mass, color = Cluster)) +
  geom_point(alpha = 0.7) +
  facet_wrap(Expt ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_size_continuous(range = c(0.25,3)) +
  theme_AGL
mp <- ggarrange(mp1, mp2, ncol = 1, nrow = 2)
ggsave("Figure_09.png", mp, width = 9, height = 6)
```

# DTF beanplot

```{r}
xx <- su17_f %>% filter(Trait == "DTF") %>%
  left_join(select(read.csv("myPCA.csv"), Name, Cluster), by = "Name")
ggplot(xx, aes(x = "Su17", y = Value)) +
  geom_beeswarm(data = xx %>% filter(Cluster == 1), side = 1L,
                color = myColors_Cluster[1]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 2), side = -1L,
                color = myColors_Cluster[2]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 3), side = 1L,
                color = myColors_Cluster[3]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 4), side = -1L,
                color = myColors_Cluster[4]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 5), side = 1L,
                color = myColors_Cluster[5]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 6), side = -1L,
                color = myColors_Cluster[6]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 7), side = -1L,
                color = myColors_Cluster[7]) +
  geom_beeswarm(data = xx %>% filter(Cluster == 8), side = 1L,
                color = myColors_Cluster[8])
```

---

```{r}
x1 <- it17_gc.v[[2]] %>% arrange(x.min)
x2 <- it17_f %>% filter(Trait == "Seed.Mass") %>%
  select(Plot, Value) 
x3 <- read.csv("myPCA.csv") %>%
  mutate(Cluster = factor(Cluster)) %>%
  select(Name, Cluster)
#
unique(x2$Trait)
xx <- x1 %>% 
  left_join(x2, by = "Plot") %>%
  left_join(x3, by = "Name") %>%
  #filter(Value > 150) %>%
  select(Plot, Entry, Name, Cluster, SeedMass=Value, 
         r, b, g.r, g.b, k, 
         x.min, x.mid, x.max, x.d, auc.l, auc.e ) %>%
  gather(Trait, Value, 6:ncol(.)) %>%
  group_by(Entry, Name, Cluster, Trait) %>%
  summarise(SeedMass = mean(SeedMass, na.rm = T),
            Value = mean(Value, na.rm = T)) %>%
  mutate(Adapted = ifelse(SeedMass > 150, "Adapted", "Unadapted"))
mp <- ggplot(xx, aes(x = Value, y = SeedMass, 
                     color = Cluster, alpha = Adapted)) +
  geom_point() +
  facet_wrap(Trait ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.7, 0.1)) +
  theme_AGL
ggsave("Figure_20.png", mp, width = 10, height = 7)
#
x1 <- su17_gc.v[[2]] %>% arrange(x.min)
x2 <- su17_f %>% filter(Trait == "Seed.Mass") %>%
  select(Plot, Value) 
x3 <- read.csv("myPCA.csv") %>%
  mutate(Cluster = factor(Cluster)) %>%
  select(Name, Cluster)
#
unique(x2$Trait)
xx <- x1 %>% 
  left_join(x2, by = "Plot") %>%
  left_join(x3, by = "Name") %>%
  #filter(Value > 150) %>%
  select(Plot, Entry, Name, Cluster, SeedMass=Value, 
         r, b, g.r, g.b, k,
         x.min, x.mid, x.max, x.d, auc.l, auc.e ) %>%
  gather(Trait, Value, 6:ncol(.)) %>%
  group_by(Entry, Name, Cluster, Trait) %>%
  summarise(SeedMass = mean(SeedMass, na.rm = T),
            Value = mean(Value, na.rm = T)) %>%
  mutate(Adapted = ifelse(SeedMass > 300, "Adapted", "Unadapted"))
mp <- ggplot(xx, aes(x = Value, y = SeedMass, 
                     color = Cluster, alpha = Adapted)) +
  geom_point() +
  facet_wrap(Trait ~ ., scales = "free") +
  scale_color_manual(values = myColors_Cluster) +
  scale_alpha_manual(values = c(0.7, 0.1)) +
  theme_AGL
ggsave("Figure_21.png", mp, width = 10, height = 7)
#
x1 <- it17_f %>% filter(Trait == "Seed.Mass") %>%
  select(Name, It17=Value) %>% group_by(Name) %>%
  summarise(It17 = mean(It17, na.rm = T))
x2 <- su17_f %>% filter(Trait == "Seed.Mass") %>%
  select(Name, Su17=Value) %>% group_by(Name) %>%
  summarise(Su17 = mean(Su17, na.rm = T))
x3 <- read.csv("myPCA.csv") %>%
  mutate(Cluster = factor(Cluster)) %>%
  select(Entry, Name, Cluster)
xx <- left_join(x1, x2, by = "Name") %>%
  left_join(x3, by = "Name")
mp <- ggplot(xx, aes(x = Su17, y = It17, color = Cluster,
                     key1 = Entry, key2 = Name)) +
  geom_point() +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL
mp <- ggplotly(mp)
saveWidget(mp, file="Figure_25.html")
#
```


```{r}
y1 <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_tb_pc_raw.csv") %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt)) %>%
  filter(ExptShort %in% c("It17","Su16","Su17","Su18","Ro16","Ro17")) %>%
  select(Plot, Tb, Pc)
y2 <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_pca_results.csv") %>%
  select(Entry, Name, Origin, Cluster, PC1, PC2, PC3, PC4, PC5, PC6)
#
y3 <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/model_t%2Bp_coefs.csv") %>%
  select(Entry, Name, a,b,c)
#
x1 <- left_join(it17_gc.a[[2]] %>% select(Plot, Name, Expt, Area=k),
                it17_gc.h[[2]] %>% select(Plot, Height=k), by = "Plot") %>%
  left_join(it17_gc.v[[2]] %>% select(Plot, Volume=k))
x2 <- left_join(ro17_gc.a[[2]] %>% select(Plot, Name, Expt, Area=k),
                ro17_gc.h[[2]] %>% select(Plot, Height=k), by = "Plot") %>%
  left_join(ro17_gc.v[[2]] %>% select(Plot, Volume=k))
x3 <- left_join(su17_gc.a[[2]] %>% select(Plot, Name, Expt, Area=k),
                su17_gc.h[[2]] %>% select(Plot, Height=k), by = "Plot") %>%
  left_join(su17_gc.v[[2]] %>% select(Plot, Volume=k))
xx <- bind_rows(x1, x2, x3) %>%
  left_join(y1, by = "Plot") %>%
  left_join(y3, by = "Name") %>%
  left_join(select(myPCA, Name, Cluster), by = "Name") %>%
  select(Plot, Entry, Name, Expt, everything()) %>%
  group_by(Entry, Name, Expt, Cluster) %>%
  summarise_at(vars(Area, Height, Volume, Tb, Pc, a, b, c), funs(mean), na.rm = T)
ggplot(xx, aes(x = b, y = Volume, color = Cluster)) +
  geom_point() +
  scale_color_manual(values = myColors_Cluster)
#
mp <- GGally::ggpairs(xx %>% filter(Expt == "Italy 2017"), mapping = aes(color = Cluster), 
        columns = c("Area", "Height", "Volume", "Tb", "Pc", "a", "b", "c")) +
  theme_AGL +
  scale_color_manual(values = myColors_Cluster)
ggsave("Figure_30_1.png", mp, width = 15, height = 15, dpi = 600)
mp <- GGally::ggpairs(xx %>% filter(Expt == "Sutherland 2017"), mapping = aes(color = Cluster), 
        columns = c("Area", "Height", "Volume", "Tb", "Pc", "a", "b", "c")) +
  theme_AGL +
  scale_color_manual(values = myColors_Cluster)
ggsave("Figure_30_2.png", mp, width = 15, height = 15, dpi = 600)
mp <- GGally::ggpairs(xx %>% filter(Expt == "Rosthern 2017"), mapping = aes(color = Cluster), 
        columns = c("Area", "Height", "Volume", "Tb", "Pc", "a", "b", "c")) +
  theme_AGL +
  scale_color_manual(values = myColors_Cluster)
ggsave("Figure_30_3.png", mp, width = 15, height = 15, dpi = 600)
#
yy <- xx %>% select(-Tb, -Pc) %>%
  gather(Trait, Value, Area, Height, Volume) %>% spread(Expt, Value) %>%
  mutate(EnvChange = `Italy 2017` - `Sutherland 2017`)
mp <- ggplot(yy, aes(x = Cluster, y = EnvChange, color = Cluster)) +
  geom_point() + theme_AGL +
  facet_wrap(. ~ Trait) +#, scales = "free_y") +
  scale_color_manual(values = myColors_Cluster)
ggsave("Figure_30_4.png", mp, width = 10, height = 6, dpi = 600)
yy <- yy %>% select(Name, Cluster, Trait, b,c, EnvChange) %>%
  spread(Trait, EnvChange)
myMin <- min(c(yy$Area,yy$Height))
myMax <- max(c(yy$Area,yy$Height))
mp <- ggplot(yy, aes(x = Area, y = Height, color = Cluster)) +
  geom_point(alpha = 0.7) + theme_AGL +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  #facet_wrap(. ~ Trait) +#, scales = "free_y") +
  scale_color_manual(values = myColors_Cluster) +
  labs(x = "Change in Area (it17 - su17)",
       y = "Change in Height (it17 - su17)")
ggsave("Figure_30_5.png", mp, width = 10, height = 3, dpi = 600)
mp <- mp + ylim(c(myMin,myMax)) + xlim(c(myMin,myMax)) 
ggsave("Figure_30_6.png", mp, width = 6, height = 4, dpi = 600)
yy <- yy %>% left_join(
  myPCAinput %>% rownames_to_column("Name") %>% 
    select(Name, It17_v.perc.DTF, Su17_v.perc.DTF), by = "Name" ) %>%
  mutate(v.perc.DTF = It17_v.perc.DTF - Su17_v.perc.DTF)
#
mp <- ggplot(yy %>% filter(!Entry %in% c(94,105)), 
             aes(x = Area, y = Height, color = Cluster, size = c*10000)) +
  geom_point(alpha = 0.7) + theme_AGL +
  geom_vline(xintercept = 0, size = 2) +
  geom_hline(yintercept = 0, size = 2) +
  #facet_wrap(. ~ Trait) +#, scales = "free_y") +
  scale_color_manual(values = myColors_Cluster) +
  scale_size_continuous(range = c(0.5, 3)) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Change in Area (it17 - su17)",
       y = "Change in Height (it17 - su17)")
ggsave("Figure_30_7.png", mp, width = 6, height = 4, dpi = 600)
#
y2 <- yy %>% ungroup() %>%
  select(Name, Cluster, It17_v.perc.DTF, Su17_v.perc.DTF) %>%
  gather(Expt, Value, 3:4)
  
mp <- ggplot(y2, aes(x = Expt, y = Value, color = Cluster)) +
  geom_beeswarm(cex = 1, alpha = 0.7) +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL +
  labs(y = "Percent growth by DTF")
ggsave("Figure_30_8.png", mp, width = 6, height = 4, dpi = 600)
```

```{r}
# Prep data
#myG <- c("G1","G2","G3","G4","G5","G6","G7","G8", "Mix")
library(rworldmap)
yy <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_countries.csv") %>% 
  select(Origin=Country, Lat, Lon)
xx <- myPCA %>%
  left_join(yy, by = "Origin") %>%
  filter(!Origin %in% c("ICARDA","USDA","Unknown")) %>% 
  group_by(Origin, Cluster, Lat, Lon) %>% 
  summarise(Count = n()) %>% 
  spread(Cluster, Count) %>%
  as.data.frame()
# Plot
png("Figure_40.png", width = 3600, height = 2055, res = 600)
par(mai = c(0,0,0,0), xaxs = "i", yaxs = "i")
mapPies(dF = xx, nameX = "Lon", nameY = "Lat", 
        zColours = myColors_Cluster, nameZs = as.character(1:8), lwd = 1,
        xlim = c(-140,110), ylim = c(5,20), addCatLegend = F,
        oceanCol = "grey90", landCol = "white", borderCol = "black") 
legend(-138.5, 15.5, title = "PCA Cluster", legend = as.character(1:8), 
       col = myColors_Cluster, pch = 16, cex = 0.8, pt.cex = 1.25, box.lwd = 2)
dev.off()
```

# END END END END END END

---

```{r}
ggGrowthCurve2 <- function(xpm, myTitle = NULL, xpca, 
                           myColors = myColors_Cluster ) {
  #
  if(sum(colnames(xpm)=="Expt")==0) { xpm <- xpm %>% mutate(Expt = myTitle) }
  xpe <- xpm %>% left_join(select(xpca, Entry, Cluster), by = "Entry") %>%
    group_by(Expt, DAP, Cluster) %>%
    summarise(Predicted.Values = mean(Predicted.Values))
  mp <- ggplot(xpm, aes(x = DAP, y = Predicted.Values)) +
    geom_line(aes(group = Entry), alpha = 0.05) +
    geom_line(data = xpe, size = 2, aes(color = Cluster)) +
    facet_grid(. ~ Expt, scales = "free_x", space = "free_x") +
    scale_color_manual(name = NULL, values = myColors) +
    theme_AGL +
    guides(color = guide_legend(nrow = 1)) +
    labs(x = "Days After Planting")
  mp
}
mp1 <- ggGrowthCurve2(xpm = it17_gc.v[[4]], xpca = myPCA,
                     myTitle = "Italy 2017 - Volume")
mp2 <- ggGrowthCurve2(xpm = it17_gc.h[[4]], xpca = myPCA,
                     myTitle = "Italy 2017 - Height")
mp3 <- ggGrowthCurve2(xpm = it17_gc.a[[4]], xpca = myPCA,
                     myTitle = "Italy 2017 - Area")
#
mp4 <- ggGrowthCurve2(xpm = su17_gc.v[[4]], xpca = myPCA,
                     myTitle = "Sutherland 2017 - Volume")
mp5 <- ggGrowthCurve2(xpm = su17_gc.h[[4]], xpca = myPCA,
                     myTitle = "Sutherland 2017 - Height")
mp6 <- ggGrowthCurve2(xpm = su17_gc.a[[4]], xpca = myPCA,
                     myTitle = "Sutherland 2017 - Area")
mp <- ggarrange(mp1, mp4, mp2, mp5, mp3, mp6, ncol = 2, nrow = 3, common.legend = T)
ggsave("Figure_04_3.png", mp, width = 12, height = 12, dpi = 600, bg = "white")
mp <- ggarrange(mp2, mp5, mp3, mp6, ncol = 2, nrow = 2, common.legend = T)
ggsave("Figure_04_4.png", mp, width = 12, height = 12, dpi = 600, bg = "white")
```

# Figure 07

```{r}
ggGrowthCurver <- function(xg, xf, myEntry, yMax, yLab) {
  if(is.null(yMax)) { yMax <- max(xg[[1]]$Value_f, na.rm = T) }
  xMax <- max(xg[[1]]$DAP, na.rm = T)
  xp <- xg[[3]] %>% filter(Entry == myEntry)
  xpm <- xp %>% group_by(Entry, Name, DAP) %>%
      summarise(Predicted.Values = mean(Predicted.Values, na.rm = T))
  xd <- xg[[1]] %>% filter(Entry == myEntry)
  xf <- xf %>% filter(Entry == myEntry)
  #
  xdtf <- xf %>% filter(Trait == "DTF")
  xdtm <- xf %>% filter(Trait == "DTM") 
  xdtf2 <- xdtf %>% group_by(Entry) %>% summarise(Value = mean(Value, na.rm =T))
  xdtm2 <- xdtm %>% group_by(Entry) %>% summarise(Value = mean(Value, na.rm =T))
  myDays <- min(xd$DAP):max(xd$DAP)  
  #
  myTitle <- unique(paste("Entry", stringr::str_pad(xd$Entry, 3, pad = "0"), "|", xd$Name))
  mp1 <- ggplot(xd, aes(x = DAP)) +
    geom_vline(data = xdtf, aes(xintercept = Value), color = "darkgreen", size = 1, alpha = 0.5) +
    #geom_vline(data = xdtm, aes(xintercept = Value), color = "darkorange", alpha = 0.5) +
    geom_point(aes(y = Value_f), color = "red", alpha = 0.7) +
    geom_point(data = xd %>% filter(!is.na(Value_f)), aes(y = Value), alpha = 0.5) +
    #geom_point(aes(y = Value), alpha = 0.5) +
    geom_line(data = xp, aes(y = Predicted.Values), alpha = 0.8) +
    facet_grid(. ~ paste("Rep", Rep, "- Plot", Plot)) +
    coord_cartesian(ylim = c(0,yMax), xlim = c(0,xMax)) +
    theme_AGL +
    labs(title = myTitle, y = yLab)
  mp2 <- ggplot(xp, aes(x = DAP, y = Predicted.Values)) +
    geom_vline(data = xdtf2, aes(xintercept = Value), color = "darkgreen", size = 1, alpha = 0.5) +
    #geom_vline(data = xdtm2, aes(xintercept = Value), color = "darkorange", alpha = 0.5) +
    geom_line(alpha = 0.3, aes(group = Plot)) +
    #geom_line(data = g2, color = "blue") +
    geom_line(data = xpm, color = "red") +
    facet_grid(. ~ "Average") +
    coord_cartesian(ylim = c(0,yMax), xlim = c(0,xMax)) +
    theme_AGL +
    labs(title = "")
  ggarrange(mp1, mp2, widths = c(1,0.5))
}
mp1 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 209, yMax = 0.65, yLab = "Ro17 - Volume")
#mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 221, yMax = 0.65)
mp3 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 105, yMax = 0.65, yLab = "Ro17 - Volume")
mp <- ggarrange(mp1,  mp3, ncol = 1)#mp2,
ggsave("Figure_07.png", mp, width = 10.6, height = 6)
# 81, 83, 50
mp1 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 209, yMax = 0.65, yLab = "It17 - Volume")
#mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 221, yMax = 0.65)
mp3 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 105, yMax = 0.65, yLab = "It17 - Volume")
mp <- ggarrange(mp1,  mp3, ncol = 1)#mp2,
ggsave("Figure_08.png", mp, width = 10.6, height = 6)
xx <- it17_f %>% filter(Trait == "DTF")
# 250, 311, 295

mp1 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 250, 
                      yMax = 0.75, yLab = "Italy 2017 Volume")
mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 250, 
                      yMax = 0.75, yLab = "Rosthern 2017 Volume")
mp <- ggarrange(mp1, mp2, ncol = 1)
ggsave("Figure_08_1.png", mp, width = 10.6, height = 6)
#
mp1 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 311, 
                      yMax = 0.75, yLab = "Italy 2017 Volume")
mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 311, 
                      yMax = 0.75, yLab = "Rosthern 2017 Volume")
mp <- ggarrange(mp1, mp2, ncol = 1)
ggsave("Figure_08_2.png", mp, width = 10.6, height = 6)
#
mp1 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 295, 
                      yMax = 0.75, yLab = "Italy 2017 Volume")
mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 295, 
                      yMax = 0.75, yLab = "Rosthern 2017 Volume")
mp <- ggarrange(mp1, mp2, ncol = 1)
ggsave("Figure_08_3.png", mp, width = 10.6, height = 6)
#
mp1 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 221, 
                      yMax = 0.75, yLab = "Italy 2017 Volume")
mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 221, 
                      yMax = 0.75, yLab = "Rosthern 2017 Volume")
mp <- ggarrange(mp1, mp2, ncol = 1)
ggsave("Figure_08_4.png", mp, width = 10.6, height = 6)
#
mp1 <- ggGrowthCurver(xg = it17_gc.v, xf = it17_f, myEntry = 205, 
                      yMax = 0.85, yLab = "Italy 2017 Volume")
mp2 <- ggGrowthCurver(xg = ro17_gc.v, xf = ro17_f, myEntry = 205, 
                      yMax = 0.85, yLab = "Rosthern 2017 Volume")
mp <- ggarrange(mp1, mp2, ncol = 1)
ggsave("Figure_08_5.png", mp, width = 10.6, height = 6)
```

---

# Adapted

```{r}
# Function
adapted_LDP <- function(xF, xV, exptname) {
  xx <- left_join(xF %>% filter(Trait %in% c("DTF","Seed.Mass")) %>%
                  select(Plot, Entry, Name, Trait, Value) %>%
                  spread(Trait, Value),
                xV[[2]] %>% select(Plot, k), by = "Plot") %>% 
    group_by(Entry, Name) %>% 
    summarise_at(vars(DTF, Seed.Mass, k), funs(mean), na.rm = T) %>%
    ungroup()
  yy <- xx %>% filter(grepl("CDC|Laird|Eston|Indian", Name)) %>%
    filter(!grepl("Gold", Name))
  xx <- xx %>% 
    mutate(Expt = exptname,
           Adapted = ifelse(DTF >= min(yy$DTF) & Seed.Mass >= min(yy$Seed.Mass) & k >= min(yy$k),
                            "Adapted", "Unadapted")) %>%
    select(Expt, Entry, Name, DTF, Seed.Mass, Volume=k, Adapted)
}
#
x1 <- adapted_LDP(xF = ro17_f, xV = ro17_gc.v, exptname = "Ro17") %>% arrange(Adapted, DTF, Seed.Mass, Volume)
x2 <- adapted_LDP(xF = su17_f, xV = su17_gc.v, exptname = "Su17") %>% arrange(Adapted, DTF, Seed.Mass, Volume)
x3 <- adapted_LDP(xF = su18_f, xV = su18_gc.v, exptname = "Su18") %>% arrange(Adapted, DTF, Seed.Mass, Volume)
x4 <- left_join(select(x1, Entry, Name, ro17_Adapted=Adapted),
                x2 %>% select(Name, su17_Adapted=Adapted), by = "Name") %>%
  left_join(select(x3, Name, su18_Adapted=Adapted), by = "Name") %>%
  mutate(All3 = ifelse(ro17_Adapted=="Adapted" & su17_Adapted=="Adapted" & su18_Adapted=="Adapted",
         "Adapted", "Unadapted")) %>%
  arrange(Entry)
writexl::write_xlsx(list(x4,x1,x2,x3), "LDP_Adapted.xlsx")
```


# PCA

```{r}
phenolGrowth <- function(xd, xf) {
  xf1 <- xf %>% filter(Trait == "DTF") %>% select(Plot, DTF=Value)
  xf2 <- xf %>% filter(Trait == "DTM") %>% select(Plot, DTM=Value)
  xd %>% 
    left_join(xf1, by = "Plot") %>%
    left_join(xf2, by = "Plot") %>%
    mutate(xmid.DTF = x.mid - DTF,
           xmax.DTF = x.max - DTF,
           perc.DTF = 100 * (k / (1 + ((k - y0) / y0) * exp(-r * DTF))) / k,
           xmid.DTM = DTM - x.mid,
           xmax.DTM = DTM - x.max) %>%
    select(Plot, xmid.DTF, xmax.DTF, perc.DTF, xmid.DTM, xmax.DTM)
}
pca_gc <- function(xx, clustNum = 8) {
  mypca <- PCA(xx, ncp = 10, graph = F)
  mypcaH <- HCPC(mypca, nb.clust = clustNum, graph = F)
  perc <- round(mypca[[1]][,2], 1)
  x1 <- mypcaH[[1]] %>% rownames_to_column("Name")
  x2 <- mypca[[3]]$coord %>% as.data.frame() %>% rownames_to_column("Name")
  pca <- left_join(x1, x2, by = "Name") %>%
    select(Name, Cluster=clust,
           PC1=Dim.1, PC2=Dim.2, PC3=Dim.3, PC4=Dim.4)
  pca
}
```

## It17 + Su17 + Ro17

```{r}
#
myColors_Cluster <- c("darkred", "darkorange3", "darkblue", "deeppink3",
                      "steelblue", "darkorchid4", "aquamarine4", "darkgreen")
myClustnum = 8
#
x1 <- it17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = it17_gc.v[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("It17_v.", colnames(x1)[4:ncol(x1)])
x2 <- it17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.a[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("It17_a.", colnames(x2)[4:ncol(x2)])
x3 <- it17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.h[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("It17_h.", colnames(x3)[4:ncol(x3)])
myX1 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- su17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = su17_gc.v[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("Su17_v.", colnames(x1)[4:ncol(x1)])
x2 <- su17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = su17_gc.a[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("Su17_a.", colnames(x2)[4:ncol(x2)])
x3 <- su17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = su17_gc.h[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("Su17_h.", colnames(x3)[4:ncol(x3)])
myX2 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- ro17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = ro17_gc.v[[2]], xf = ro17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("Ro17_v.", colnames(x1)[4:ncol(x1)])
x2 <- ro17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = ro17_gc.a[[2]], xf = ro17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("Ro17_a.", colnames(x2)[4:ncol(x2)])
x3 <- ro17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = ro17_gc.h[[2]], xf = ro17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("Ro17_h.", colnames(x3)[4:ncol(x3)])
myX3 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
myPCAinput <- left_join(myX1, myX2, by = "Name") %>%
  left_join(myX3, by = "Name") %>%
  column_to_rownames("Name")
sum(is.na(myPCAinput))
#
myPCA <- pca_gc(xx = myPCAinput, clustNum = myClustnum) %>%
  left_join(myLDP, by = "Name") %>% select(Entry, Name, Origin, Region, everything())
write.csv(myPCA, "myPCA.csv", row.names = F)
write.csv(myPCAinput, "myPCAinput.csv", row.names = F)
#
myTraits1 <- c("It17_v.k", "It17_h.k", "It17_a.k", "It17_v.x.mid", "It17_h.x.mid", "It17_a.x.mid",
               "Su17_v.k", "Su17_h.k", "Su17_a.k", "Su17_v.x.mid", "Su17_h.x.mid", "Su17_a.x.mid",
               "Ro17_v.k", "Ro17_h.k", "Ro17_a.k", "Ro17_v.x.mid", "Ro17_h.x.mid", "Ro17_a.x.mid",
               #
               "It17_v.perc.DTF", "It17_h.perc.DTF", "It17_a.perc.DTF",
               "It17_v.xmax.DTF", "It17_h.xmax.DTF", "It17_a.xmax.DTF", 
               "Su17_v.perc.DTF", "Su17_h.perc.DTF", "Su17_a.perc.DTF",
               "Su17_v.xmax.DTF", "Su17_h.xmax.DTF", "Su17_a.xmax.DTF",
               "Ro17_v.perc.DTF", "Ro17_h.perc.DTF", "Ro17_a.perc.DTF",
               "Ro17_v.xmax.DTF", "Ro17_h.xmax.DTF", "Ro17_a.xmax.DTF",
               #
               #"It17_v.g.r", "It17_h.g.r", "It17_a.g.r", 
               #"Su17_v.g.r", "Su17_h.g.r", "Su17_a.g.r", 
               #"Ro17_v.g.r", "Ro17_h.g.r", "Ro17_a.g.r",
               #
               "It17_v.x.d", "It17_h.x.d", "It17_a.x.d",
               "Su17_v.x.d", "Su17_h.x.d", "Su17_a.x.d",
               "Ro17_v.x.d", "Ro17_h.x.d", "Ro17_a.x.d" 
               )
xx <- myPCAinput %>% rownames_to_column("Name") %>%
  left_join(select(myPCA, Entry, Name, Origin, Cluster), by = "Name") %>%
  select(Entry, Name, Origin, Cluster, everything()) %>%
  gather(Trait, Value, 5:ncol(.)) %>%
  mutate(Trait = factor(Trait, levels = myTraits1))
mp <- ggplot(xx, aes(x = Cluster, y = Value, color = Cluster)) +
  geom_quasirandom(alpha = 0.7) +
  facet_wrap(Trait ~ ., scales = "free_y", ncol = 6) +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL
ggsave("Figure_05_t1.png", mp, width = 15, height = 14)
```

## It17 + Su17

```{r}
#
myColors_Cluster <- c("darkred", "darkorange3", "darkblue", "deeppink3",
                      "steelblue", "darkorchid4", "cornsilk4", "darkgreen")
myClustnum = 8
#
x1 <- it17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = it17_gc.v[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("It17_v.", colnames(x1)[4:ncol(x1)])
x2 <- it17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.a[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("It17_a.", colnames(x2)[4:ncol(x2)])
x3 <- it17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.h[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("It17_h.", colnames(x3)[4:ncol(x3)])
myX1 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- su17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = su17_gc.v[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("Su17_v.", colnames(x1)[4:ncol(x1)])
x2 <- su17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = su17_gc.a[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("Su17_a.", colnames(x2)[4:ncol(x2)])
x3 <- su17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = su17_gc.h[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("Su17_h.", colnames(x3)[4:ncol(x3)])
myX2 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
myPCAinput <- left_join(myX1, myX2, by = "Name") %>%
  column_to_rownames("Name")
sum(is.na(myPCAinput))
#
myPCA <- pca_gc(xx = myPCAinput, clustNum = myClustnum) %>%
  left_join(myLDP, by = "Name") %>% select(Entry, Name, Origin, Region, everything())
write.csv(myPCA, "myPCA.csv", row.names = F)
write.csv(myPCAinput, "myPCAinput.csv", row.names = F)
#
myTraits1 <- c("It17_v.k", "It17_h.k", "It17_a.k", "It17_v.x.mid", "It17_h.x.mid", "It17_a.x.mid",
               "Su17_v.k", "Su17_h.k", "Su17_a.k", "Su17_v.x.mid", "Su17_h.x.mid", "Su17_a.x.mid",
               "Ro17_v.k", "Ro17_h.k", "Ro17_a.k", "Ro17_v.x.mid", "Ro17_h.x.mid", "Ro17_a.x.mid",
               #
               "It17_v.perc.DTF", "It17_h.perc.DTF", "It17_a.perc.DTF",
               "It17_v.xmax.DTF", "It17_h.xmax.DTF", "It17_a.xmax.DTF", 
               "Su17_v.perc.DTF", "Su17_h.perc.DTF", "Su17_a.perc.DTF",
               "Su17_v.xmax.DTF", "Su17_h.xmax.DTF", "Su17_a.xmax.DTF",
               "Ro17_v.perc.DTF", "Ro17_h.perc.DTF", "Ro17_a.perc.DTF",
               "Ro17_v.xmax.DTF", "Ro17_h.xmax.DTF", "Ro17_a.xmax.DTF",
               #
               #"It17_v.g.r", "It17_h.g.r", "It17_a.g.r", 
               #"Su17_v.g.r", "Su17_h.g.r", "Su17_a.g.r", 
               #"Ro17_v.g.r", "Ro17_h.g.r", "Ro17_a.g.r",
               #
               "It17_v.x.d", "It17_h.x.d", "It17_a.x.d",
               "Su17_v.x.d", "Su17_h.x.d", "Su17_a.x.d",
               "Ro17_v.x.d", "Ro17_h.x.d", "Ro17_a.x.d" 
               )
xx <- myPCAinput %>% rownames_to_column("Name") %>%
  left_join(select(myPCA, Entry, Name, Origin, Cluster), by = "Name") %>%
  select(Entry, Name, Origin, Cluster, everything()) %>%
  gather(Trait, Value, 5:ncol(.)) %>%
  mutate(Trait = factor(Trait, levels = myTraits1))
mp <- ggplot(xx, aes(x = Cluster, y = Value, color = Cluster)) +
  geom_quasirandom(alpha = 0.7) +
  facet_wrap(Trait ~ ., scales = "free_y", ncol = 6) +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL
ggsave("Figure_05_t2.png", mp, width = 15, height = 14)
```

## It17 + Ro17

```{r}
#
myColors_Cluster <- c("darkred", "darkorange3", "darkblue", "deeppink3",
                      "steelblue", "darkorchid4", "cornsilk4", "darkgreen")
myClustnum = 8
#
x1 <- it17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = it17_gc.v[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("It17_v.", colnames(x1)[4:ncol(x1)])
x2 <- it17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.a[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("It17_a.", colnames(x2)[4:ncol(x2)])
x3 <- it17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.h[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("It17_h.", colnames(x3)[4:ncol(x3)])
myX1 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- ro17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = ro17_gc.v[[2]], xf = ro17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("Ro17_v.", colnames(x1)[4:ncol(x1)])
x2 <- ro17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = ro17_gc.a[[2]], xf = ro17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("Ro17_a.", colnames(x2)[4:ncol(x2)])
x3 <- ro17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = ro17_gc.h[[2]], xf = ro17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("Ro17_h.", colnames(x3)[4:ncol(x3)])
myX2 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
myPCAinput <- left_join(myX1, myX2, by = "Name") %>%
  column_to_rownames("Name")
sum(is.na(myPCAinput))
#
myPCA <- pca_gc(xx = myPCAinput, clustNum = myClustnum) %>%
  left_join(myLDP, by = "Name") %>% select(Entry, Name, Origin, Region, everything())
write.csv(myPCA, "myPCA.csv", row.names = F)
write.csv(myPCAinput, "myPCAinput.csv", row.names = F)
#
myTraits1 <- c("It17_v.k", "It17_h.k", "It17_a.k", "It17_v.x.mid", "It17_h.x.mid", "It17_a.x.mid",
               "Su17_v.k", "Su17_h.k", "Su17_a.k", "Su17_v.x.mid", "Su17_h.x.mid", "Su17_a.x.mid",
               "Ro17_v.k", "Ro17_h.k", "Ro17_a.k", "Ro17_v.x.mid", "Ro17_h.x.mid", "Ro17_a.x.mid",
               #
               "It17_v.perc.DTF", "It17_h.perc.DTF", "It17_a.perc.DTF",
               "It17_v.xmax.DTF", "It17_h.xmax.DTF", "It17_a.xmax.DTF", 
               "Su17_v.perc.DTF", "Su17_h.perc.DTF", "Su17_a.perc.DTF",
               "Su17_v.xmax.DTF", "Su17_h.xmax.DTF", "Su17_a.xmax.DTF",
               "Ro17_v.perc.DTF", "Ro17_h.perc.DTF", "Ro17_a.perc.DTF",
               "Ro17_v.xmax.DTF", "Ro17_h.xmax.DTF", "Ro17_a.xmax.DTF",
               #
               #"It17_v.g.r", "It17_h.g.r", "It17_a.g.r", 
               #"Su17_v.g.r", "Su17_h.g.r", "Su17_a.g.r", 
               #"Ro17_v.g.r", "Ro17_h.g.r", "Ro17_a.g.r",
               #
               "It17_v.x.d", "It17_h.x.d", "It17_a.x.d",
               "Su17_v.x.d", "Su17_h.x.d", "Su17_a.x.d",
               "Ro17_v.x.d", "Ro17_h.x.d", "Ro17_a.x.d" 
               )
xx <- myPCAinput %>% rownames_to_column("Name") %>%
  left_join(select(myPCA, Entry, Name, Origin, Cluster), by = "Name") %>%
  select(Entry, Name, Origin, Cluster, everything()) %>%
  gather(Trait, Value, 5:ncol(.)) %>%
  mutate(Trait = factor(Trait, levels = myTraits1))
mp <- ggplot(xx, aes(x = Cluster, y = Value, color = Cluster)) +
  geom_quasirandom(alpha = 0.7) +
  facet_wrap(Trait ~ ., scales = "free_y", ncol = 6) +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL
ggsave("Figure_05_t3.png", mp, width = 15, height = 14)
```

---

## GDD

```{r}
#
myColors_Cluster <- c("darkred", "darkorange3", "darkblue", "deeppink3",
                      "steelblue", "darkorchid4", "cornsilk4", "darkgreen")
myClustnum = 8
#
x1 <- it17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = it17_gc.v[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("It17_v.", colnames(x1)[4:ncol(x1)])
x2 <- it17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.a[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("It17_a.", colnames(x2)[4:ncol(x2)])
x3 <- it17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = it17_gc.h[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("It17_h.", colnames(x3)[4:ncol(x3)])
myX1 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- su17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>% #g.r
  left_join(phenolGrowth(xd = su17_gc.v[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("Su17_v.", colnames(x1)[4:ncol(x1)])
x2 <- su17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = su17_gc.a[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x2)[4:ncol(x2)] <- paste0("Su17_a.", colnames(x2)[4:ncol(x2)])
x3 <- su17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid, x.d) %>%
  left_join(phenolGrowth(xd = su17_gc.h[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x3)[4:ncol(x3)] <- paste0("Su17_h.", colnames(x3)[4:ncol(x3)])
myX2 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- it17_gdd.v %>% select(Plot, Entry, Name, GDD.mid, GDD.max, GDD.max.DTF)
#PPD.mid, PPD.max,, PPD.max.DTF)
colnames(x1)[4:ncol(x1)] <- paste0("It17_v.", colnames(x1)[4:ncol(x1)])
x2 <- it17_gdd.h %>% select(Plot, Entry, Name, GDD.mid, GDD.max) #, PPD.mid, PPD.max
colnames(x2)[4:ncol(x2)] <- paste0("It17_h.", colnames(x2)[4:ncol(x2)])
x3 <- it17_gdd.a %>% select(Plot, Entry, Name, GDD.mid, GDD.max) #, PPD.mid, PPD.max
colnames(x3)[4:ncol(x3)] <- paste0("It17_a.", colnames(x3)[4:ncol(x3)])
myX3 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
x1 <- su17_gdd.v %>% select(Plot, Entry, Name, GDD.mid, GDD.max, GDD.max.DTF) 
# PPD.mid, PPD.max, PPD.max.DTF
colnames(x1)[4:ncol(x1)] <- paste0("Su17_v.", colnames(x1)[4:ncol(x1)])
x2 <- su17_gdd.h %>% select(Plot, Entry, Name, GDD.mid, GDD.max) #, PPD.mid, PPD.max
colnames(x2)[4:ncol(x2)] <- paste0("Su17_h.", colnames(x2)[4:ncol(x2)])
x3 <- su17_gdd.a %>% select(Plot, Entry, Name, GDD.mid, GDD.max) #, PPD.mid, PPD.max
colnames(x3)[4:ncol(x3)] <- paste0("Su17_a.", colnames(x3)[4:ncol(x3)])
myX4 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
#
myPCAinput <- left_join(myX1, myX2, by = "Name") %>%
  #left_join(myX3, by = "Name") %>%
  #left_join(myX4, by = "Name") %>%
  column_to_rownames("Name")
sum(is.na(myPCAinput))
#
myPCA <- pca_gc(xx = myPCAinput, clustNum = myClustnum) %>%
  left_join(myLDP, by = "Name") %>% select(Entry, Name, Origin, Region, everything())
write.csv(myPCA, "myPCA.csv", row.names = F)
write.csv(myPCAinput, "myPCAinput.csv", row.names = F)
#
myTraits1 <- c("It17_v.k", "It17_h.k", "It17_a.k", "It17_v.x.mid", "It17_h.x.mid", "It17_a.x.mid",
               "Su17_v.k", "Su17_h.k", "Su17_a.k", "Su17_v.x.mid", "Su17_h.x.mid", "Su17_a.x.mid",
               "It17_v.g.r", "Su17_v.g.r",
               "It17_v.perc.DTF", "It17_h.perc.DTF", "It17_a.perc.DTF",
               "It17_v.xmax.DTF", "It17_h.xmax.DTF", "It17_a.xmax.DTF", 
               "Su17_v.perc.DTF", "Su17_h.perc.DTF", "Su17_a.perc.DTF",
               "Su17_v.xmax.DTF", "Su17_h.xmax.DTF", "Su17_a.xmax.DTF",
               #
               "It17_v.x.d", "It17_h.x.d", "It17_a.x.d", 
               "Su17_v.x.d", "Su17_h.x.d", "Su17_a.x.d", 
               #
               "It17_v.GDD.mid", "It17_v.GDD.max", "It17_v.PPD.mid", "It17_v.PPD.max",
               "It17_v.GDD.max.DTF", "It17_v.PPD.max.DTF",
               "It17_a.GDD.mid", "It17_a.GDD.max", "It17_a.PPD.mid", "It17_a.PPD.max",
               "It17_h.GDD.mid", "It17_h.GDD.max", "It17_h.PPD.mid", "It17_h.PPD.max",
               #
               "Su17_v.GDD.mid", "Su17_v.GDD.max", "Su17_v.PPD.mid", "Su17_v.PPD.max",
               "Su17_v.GDD.max.DTF", "Su17_v.PPD.max.DTF",
               "Su17_a.GDD.mid", "Su17_a.GDD.max", "Su17_a.PPD.mid", "Su17_a.PPD.max",
               "Su17_h.GDD.mid", "Su17_h.GDD.max", "Su17_h.PPD.mid", "Su17_h.PPD.max" 
               )
xx <- myPCAinput %>% rownames_to_column("Name") %>%
  left_join(select(myPCA, Entry, Name, Origin, Cluster), by = "Name") %>%
  select(Entry, Name, Origin, Cluster, everything()) %>%
  gather(Trait, Value, 5:ncol(.)) %>%
  mutate(Trait = factor(Trait, levels = myTraits1))
mp <- ggplot(xx, aes(x = Cluster, y = Value, color = Cluster)) +
  geom_quasirandom(alpha = 0.7) +
  facet_wrap(Trait ~ ., scales = "free_y", ncol = 6) +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL
ggsave("Figure_05.png", mp, width = 12, height = 8)
```

```{r}
#
myColors_Cluster <- c("darkred", "darkorange3", "darkblue", "deeppink3",
                      "steelblue", "darkorchid4", "cornsilk4", "darkgreen")
myClustnum = 8
#
x1 <- it17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, g.r, k, x.mid) %>%
  left_join(phenolGrowth(xd = it17_gc.v[[2]], xf = it17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x1)[4:ncol(x1)] <- paste0("It17_v.", colnames(x1)[4:ncol(x1)])
x2 <- it17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid)
colnames(x2)[4:ncol(x2)] <- paste0("It17_a.", colnames(x2)[4:ncol(x2)])
x3 <- it17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid)
colnames(x3)[4:ncol(x3)] <- paste0("It17_h.", colnames(x3)[4:ncol(x3)])
#
x4 <- su17_gc.v[[2]] %>% 
  select(Plot, Entry, Name, g.r, k, x.mid) %>%
  left_join(phenolGrowth(xd = su17_gc.v[[2]], xf = su17_f), by = "Plot") %>% 
  select(-xmid.DTF, -xmid.DTM, -xmax.DTM)
colnames(x4)[4:ncol(x4)] <- paste0("Su17_v.", colnames(x4)[4:ncol(x4)])
x5 <- su17_gc.a[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid)
colnames(x5)[4:ncol(x5)] <- paste0("Su17_a.", colnames(x5)[4:ncol(x5)])
x6 <- su17_gc.h[[2]] %>% 
  select(Plot, Entry, Name, k, x.mid)
colnames(x6)[4:ncol(x6)] <- paste0("Su17_h.", colnames(x6)[4:ncol(x6)])
#
myX1 <- left_join(x1, x3, by = c("Plot","Entry","Name")) %>% 
  left_join(x2, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
myX2 <- left_join(x4, x6, by = c("Plot","Entry","Name")) %>% 
  left_join(x5, by = c("Plot","Entry","Name")) %>%
  select(-Plot) %>%
  gather(Trait, Value, 3:ncol(.)) %>%
  group_by(Entry, Name, Trait) %>% 
  summarise(Value = mean(Value, na.rm = T)) %>%
  ungroup() %>%
  spread(Trait, Value) %>% select(-Entry)
myPCAinput <- left_join(myX1, myX2, by = "Name") %>%
  column_to_rownames("Name")
sum(is.na(myPCAinput))
#
myPCA <- pca_gc(xx = myPCAinput, clustNum = myClustnum) %>%
  left_join(myLDP, by = "Name") %>% select(Entry, Name, Origin, Region, everything())
write.csv(myPCA, "myPCA2.csv", row.names = F)
write.csv(myPCAinput, "myPCAinput2.csv", row.names = F)
#
myTraits1 <- c("It17_v.k", "It17_h.k", "It17_a.k", "It17_v.x.mid", "It17_h.x.mid", "It17_a.x.mid",
               "Su17_v.k", "Su17_h.k", "Su17_a.k", "Su17_v.x.mid", "Su17_h.x.mid", "Su17_a.x.mid",
               "It17_v.g.r", "Su17_v.g.r", "It17_v.perc.DTF", "Su17_v.perc.DTF", 
               "It17_v.xmax.DTF", "Su17_v.xmax.DTF")
xx <- myPCAinput %>% rownames_to_column("Name") %>%
  left_join(select(myPCA, Entry, Name, Origin, Cluster), by = "Name") %>%
  select(Entry, Name, Origin, Cluster, everything()) %>%
  gather(Trait, Value, 5:ncol(.)) %>%
  mutate(Trait = factor(Trait, levels = myTraits1))
mp <- ggplot(xx, aes(x = Cluster, y = Value, color = Cluster, key1 = Entry)) +
  geom_quasirandom(alpha = 0.7) +
  facet_wrap(Trait ~ ., scales = "free_y", ncol = 6) +
  scale_color_manual(values = myColors_Cluster) +
  theme_AGL
ggsave("Figure_05_2.png", mp, width = 10.6, height = 6)
mp <- ggplotly(mp)
saveWidget(mp, file="Figure_05_2.html")
```

---

## 3D Animation

```{r}
library(plot3D) # scatter3D()
library(magick)
# Prep data
xx <- read.csv("myPCA.csv") %>% 
  mutate(Cluster = factor(Cluster), PC2 = PC2*3, PC3 = PC3*3) #,
         #myColors = plyr::mapvalues(Cluster, 1:8, myColors_Cluster))
# Create plotting function
ggPCA <- function(x = xx, i = 1) {
  # Plot
  par(mar=c(1.5, 2.5, 1.5, 0.5))
  scatter3D(x = x$PC1, y = x$PC3, z = x$PC2, pch = 16, cex = 0.75, 
    col = alpha(myColors_Cluster,0.8), colvar = as.numeric(x$Cluster), colkey = F,  
    col.grid = "gray90", bty = "u",
    theta = i, phi = 15, ticktype = "detailed", 
    cex.lab = 1, cex.axis = 0.5,
    xlab = "PC1", ylab = "PC3", zlab = "PC2", main = "PCA - LDP Growth Data")
}
# Plot each angle
for (i in seq(0, 360, by = 2)) {
  png(paste0("Additional/PCA/PCA_", str_pad(i, 3, pad = "0"), ".png"), 
      width = 1000, height = 1000, res = 300) 
  ggPCA(xx, i)
  dev.off()
}
# Create animation
lf <- list.files("Additional/PCA")
mp <- image_read(paste0("Additional/PCA/", lf))
animation <- image_animate(mp, fps = 10)
image_write(animation, "Additional/Animation_PCA.gif")
```

```{r}
library(ggdensity)
ggplot(myPCA, aes(x = PC1, y = PC2, fill = Cluster)) +
  geom_hdr() + geom_point(pch = 21) +
  scale_fill_manual(values = myColors_Cluster)
ggplot(myPCA, aes(x = PC1, y = PC2)) +
  geom_hdr(aes(group = Cluster, fill = after_stat(probs))) 

ggplot(myPCA, aes(x = PC1, y = PC2)) +
  geom_hdr_lines(aes(color = Cluster)) +
  scale_color_manual(values = myColors_Cluster)
  #geom_point(pch = 21)

ggplot(myPCA, aes(x = PC1, y = PC2, fill = Cluster)) +
  geom_hdr() + geom_density_2d(color = "black") +
  scale_fill_manual(values = myColors_Cluster)

ggplot(myPCA, aes(x = PC1, y = PC2, fill = Cluster, color = Cluster)) +
  geom_hdr() + geom_rug() +
  scale_fill_manual(values = myColors_Cluster) +
  scale_color_manual(values = myColors_Cluster)
ggplot(myPCA, aes(x = PC1, y = PC2, fill = Cluster, color = Cluster)) +
  geom_hdr() + geom_hdr_rug() +
  scale_fill_manual(values = myColors_Cluster) +
  scale_color_manual(values = myColors_Cluster)
```

---

# Correlations


```{r}
ggDroneCorr2 <- function(xd, xf, xpca, myTitle, myTrait, xLab, yLab) {
  xpca <- xpca %>% select(Entry, Cluster)
  xd <- xd[[2]] %>% group_by(Entry) %>% summarise(k = mean(k)) %>% ungroup()
  xf <- xf %>% filter(Trait == myTrait) %>% select(Plot, Entry, Name, Value)
  xx <- left_join(xf, xd, by = "Entry") %>%
    left_join(xpca, by = "Entry") %>%
    group_by(Entry, Name, Cluster)
  myCorr <- cor(xx$Value, xx$k, use = "complete.obs")^2
  ggplot(xx, aes(x = Value, y = k, color = Cluster)) +
    geom_point(alpha = 0.7) + 
    #stat_smooth(geom = "line", method = "lm", se = F, alpha = 0.7) +
    stat_smooth(geom = "line", method = "lm", se = F, 
                size = 1, alpha = 0.7, color = "black") +
    facet_grid(. ~ paste("R^2 =", as.factor(round(myCorr,2)))) +
    scale_color_manual(name = NULL, values = myColors_Cluster) +
    theme_AGL + 
    labs(title = myTitle, x = xLab, y = yLab)
}
ggDroneCorr3 <- function(xd, xf, xpca, myTitle, myTrait, xLab, yLab) {
  xpca <- xpca %>% select(Entry, Cluster)
  xd <- xd[[2]] %>% select(Plot, k)
  xf <- xf %>% filter(Trait == myTrait) %>% select(Plot, Entry, Name, Value)
  xx <- left_join(xf, xd, by = "Plot") %>%
    left_join(xpca, by = "Entry") %>%
    group_by(Entry, Name, Cluster) %>%
    summarise(Value = mean(Value, na.rm = T),
              k = mean(k, na.rm = T)) %>%
    ungroup()
  myCorr <- cor(xx$Value, xx$k, use = "complete.obs")^2
  ggplot(xx, aes(x = Value, y = k, color = Cluster)) +
    geom_point(alpha = 0.7) +
    #stat_smooth(geom = "line", method = "lm", se = F, alpha = 0.7) +
    stat_smooth(geom = "line", method = "lm", se = F, 
                size = 1, alpha = 0.7, color = "black") +
    facet_grid(. ~ paste("R^2 =", as.factor(round(myCorr,2)))) +
    scale_color_manual(name = NULL, values = myColors_Cluster) +
    theme_AGL + 
    labs(title = myTitle, x = xLab, y = yLab)
}
ggDroneCorr4 <- function(xd, xf, xpca, myTitle, myTrait, xLab, yLab) {
  xpca <- xpca %>% select(Entry, Cluster)
  xd <- xd[[2]] %>% group_by(Entry) %>% summarise(k = mean(k)) %>% ungroup()
  xf <- xf %>% select(Entry, Name, Value=myTrait)
  xx <- left_join(xf, xd, by = "Entry") %>%
    left_join(xpca, by = "Entry") %>%
    group_by(Entry, Name, Cluster)
  myCorr <- cor(xx$Value, xx$k, use = "complete.obs")
  ggplot(xx, aes(x = Value, y = k, color = Cluster)) +
    geom_point(alpha = 0.7) + 
    #stat_smooth(geom = "line", method = "lm", se = F, alpha = 0.7) +
    stat_smooth(geom = "line", method = "lm", se = F, 
                size = 1, alpha = 0.7, color = "black") +
    facet_grid(. ~ paste("R^2 =", as.factor(round(myCorr,2)))) +
    scale_color_manual(name = NULL, values = myColors_Cluster) +
    theme_AGL + 
    labs(title = myTitle, x = xLab, y = yLab)
}
```

## Italy 2017

```{r}
# Height
mp <- ggDroneCorr2(xd = it17_gc.h, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",    yLab = "Canopy Height (Drone)",
                  myTrait = "Canopy.Height", xLab = "Canopy Height (Manual)")
ggsave("Additional/ggDroneCorr_It17_Height1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = it17_gc.h, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",   yLab = "Canopy Height (Drone)", 
                  myTrait = "Plant.Length", xLab = "Plant Length (Manual)")
ggsave("Additional/ggDroneCorr_It17_Height2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = it17_gc.h, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",        yLab = "Canopy Height (Drone)", 
                  myTrait = "Lowest.Pod.Height", xLab = "Lowest Pod Height (Manual)")
ggsave("Additional/ggDroneCorr_It17_Height3.png", mp, width = 6, height = 4)
# Volume
mp <- ggDroneCorr2(xd = it17_gc.v, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",   yLab = "Plot Volume (Drone)", 
                  myTrait = "Plot.Biomass", xLab = "Plot Biomass (Manual)")
ggsave("Additional/ggDroneCorr_It17_Volume1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = it17_gc.v, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",    yLab = "Plot Volume (Drone)", 
                  myTrait = "Straw.Biomass", xLab = "Straw Biomass (Manual)")
ggsave("Additional/ggDroneCorr_It17_Volume2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = it17_gc.v, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Seed.Mass",  xLab = "Seed Yield (Manual)")
ggsave("Additional/ggDroneCorr_It17_Volume3.png", mp, width = 6, height = 4)
# Area
mp <- ggDroneCorr2(xd = it17_gc.a, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",   yLab = "Plot Area (Drone)", 
                  myTrait = "Canopy.Width", xLab = "Canopy Width (Manual)")
ggsave("Additional/ggDroneCorr_It17_Area1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = it17_gc.a, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",   yLab = "Plot Area (Drone)", 
                  myTrait = "Growth.Habit", xLab = "Growth Habit (Manual)")
ggsave("Additional/ggDroneCorr_It17_Area2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = it17_gc.a, xf = it17_f, xpca = myPCA,
                  myTitle = "Italy 2017",      yLab = "Plot Area (Drone)", 
                  myTrait = "Nodes.At.Flower", xLab = "Nodes at Flower (Manual)")
ggsave("Additional/ggDroneCorr_It17_Area3.png", mp, width = 6, height = 4)
#unique(it17_f$Trait)
mp <- ggDroneCorr4(xd = it17_gc.v, xf = myLDP, xpca = myPCA, 
                   myTitle = "Italy 2017",   yLab = "Plot Volume (Drone)", 
                   myTrait = "SeedMass1000.2017", xLab = "Thousand Seed Mass (Manual)")
ggsave("Additional/ggDroneCorr_It17_Volume4.png", mp, width = 6, height = 4)
```

## Rosthern 2017

```{r}
# Height
mp <- ggDroneCorr2(xd = ro17_gc.h, xf = ro17_f, xpca = myPCA,
                  myTitle = "Rosthern 2017", yLab = "Canopy Height (Drone)", 
                  myTrait = "Canopy.Height", xLab = "Canopy Height (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Height1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = ro17_gc.h, xf = ro17_f, xpca = myPCA,
                  myTitle = "Rosthern 2017", yLab = "Canopy Height (Drone)", 
                  myTrait = "Plant.Length",  xLab = "Canopy Height (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Height2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = ro17_gc.h, xf = ro17_f, xpca = myPCA,
                  myTitle = "Rosthern 2017",     yLab = "Canopy Height (Drone)", 
                  myTrait = "Lowest.Pod.Height", xLab = "Lowest Pod Height (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Height3.png", mp, width = 6, height = 4)
# Volume
mp <- ggDroneCorr2(xd = ro17_gc.v, xf = ro17_f, xpca = myPCA,
                  myTitle = "Rosthern 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Plot.Biomass",  xLab = "Plot Biomass (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Volume1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = ro17_gc.v, xf = ro17_f, xpca = myPCA,
                  myTitle = "Rosthern 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Straw.Biomass", xLab = "Straw Biomass (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Volume2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = ro17_gc.v, xf = ro17_f, xpca = myPCA,
                  myTitle = "Rosthern 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Seed.Mass",     xLab = "Seed Yeild (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Volume3.png", mp, width = 6, height = 4)
#unique(ro17_f$Trait)
mp <- ggDroneCorr4(xd = ro17_gc.v, xf = myLDP, xpca = myPCA, 
                   myTitle = "Rosthern 2017",   yLab = "Plot Volume (Drone)", 
                   myTrait = "SeedMass1000.2017", xLab = "Thousand Seed Mass (Manual)")
ggsave("Additional/ggDroneCorr_Ro17_Volume4.png", mp, width = 6, height = 4)
```

## Sutherland 2017

```{r}
# Height
mp <- ggDroneCorr2(xd = su17_gc.h, xf = su17_f, xpca = myPCA, 
                  myTitle = "Sutherland 2017", yLab = "Canopy Height (Drone)", 
                  myTrait = "Canopy.Height",   xLab = "Canopy Height (Manual)")
ggsave("Additional/ggDroneCorr_Su17_Height1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = su17_gc.h, xf = su17_f, xpca = myPCA, 
                  myTitle = "Sutherland 2017", yLab = "Canopy Height (Drone)", 
                  myTrait = "Plant.Length",    xLab = "Plant Length (Manual)")
ggsave("Additional/ggDroneCorr_Su17_Height2.png", mp, width = 6, height = 4)
# Volume
mp <- ggDroneCorr2(xd = su17_gc.v, xf = su17_f, xpca = myPCA, 
                   myTitle = "Sutherland 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Plot.Biomass",     xLab = "Plot Biomass (Manual)")
ggsave("Additional/ggDroneCorr_Su17_Volume1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = su17_gc.v, xf = su17_f, xpca = myPCA, 
                   myTitle = "Sutherland 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Straw.Biomass",    xLab = "Straw Biomass (Manual)")
ggsave("Additional/ggDroneCorr_Su17_Volume2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = su17_gc.v, xf = su17_f, xpca = myPCA, 
                   myTitle = "Sutherland 2017", yLab = "Plot Volume (Drone)", 
                  myTrait = "Seed.Mass",        xLab = "Seed Yield (Manual)")
ggsave("Additional/ggDroneCorr_Su17_Volume3.png", mp, width = 6, height = 4)
#unique(su17_f$Trait)
mp <- ggDroneCorr4(xd = su17_gc.v, xf = myLDP, xpca = myPCA, 
                   myTitle = "Sutherland 2017",   yLab = "Plot Volume (Drone)", 
                   myTrait = "SeedMass1000.2017", xLab = "Thousand Seed Mass (Manual)")
ggsave("Additional/ggDroneCorr_Su17_Volume4.png", mp, width = 6, height = 4)
```

## Sutherland 2018

```{r}
# Height
mp <- ggDroneCorr2(xd = su18_gc.h, xf = su18_f, xpca = myPCA, 
                  myTitle = "Sutherland 2018", yLab = "Canopy Height (Drone)", 
                  myTrait = "CanopyHeight",    xLab = "Canopy Height (Manual)")
ggsave("Additional/ggDroneCorr_Su18_Height1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = su18_gc.h, xf = su18_f, xpca = myPCA, 
                  myTitle = "Sutherland 2018", yLab = "Canopy Height (Drone)", 
                  myTrait = "Plant.Length",    xLab = "Plant Length (Manual)")
ggsave("Additional/ggDroneCorr_Su18_Height2.png", mp, width = 6, height = 4)
# Volume
mp <- ggDroneCorr2(xd = su18_gc.v, xf = su18_f, xpca = myPCA, 
                  myTitle = "Sutherland 2018", yLab = "Plot Volume (Drone)", 
                  myTrait = "Plot.Biomass",    xLab = "Plot Biomass (Manual)")
ggsave("Additional/ggDroneCorr_Su18_Volume1.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = su18_gc.v, xf = su18_f, xpca = myPCA, 
                   myTitle = "Sutherland 2018", yLab = "Plot Volume (Drone)", 
                  myTrait = "Straw.Biomass",    xLab = "Straw Biomass (Manual)")
ggsave("Additional/ggDroneCorr_Su18_Volume2.png", mp, width = 6, height = 4)
mp <- ggDroneCorr2(xd = su18_gc.v, xf = su18_f, xpca = myPCA, 
                   myTitle = "Sutherland 2018", yLab = "Plot Volume (Drone)", 
                  myTrait = "Seed.Mass",        xLab = "Seed Yield (Manual)")
ggsave("Additional/ggDroneCorr_Su18_Volume3.png", mp, width = 6, height = 4)
unique(su18_f$Trait)
#
mp <- ggDroneCorr4(xd = su18_gc.v, xf = myLDP, xpca = myPCA, 
                   myTitle = "Sutherland 2018",   yLab = "Plot Volume (Drone)", 
                   myTrait = "SeedMass1000.2018", xLab = "Thousand Seed Mass (Manual)")
ggsave("Additional/ggDroneCorr_Su18_Volume4.png", mp, width = 6, height = 4)
```



# Extra

```{r}
su18_f %>% filter(Entry == 221) %>% pull(Plot)
su18_f %>% filter(Entry == 295) %>% pull(Plot)
```

```{r}
xx <- su18_f %>% filter(Trait == "Leaf.Color") %>% 
  select(Plot, Leaf.Color=Value) %>%
  left_join(su18_d, by = "Plot") %>%
  filter(DAP == 76)
unique(xx$Trait)
mp <- ggplot(xx, aes(x = Leaf.Color, y = Value, color = as.factor(Leaf.Color))) +
  geom_quasirandom() +
  facet_wrap(Trait ~ DAP, scales = "free", ncol = 8) +
  scale_color_manual(values = c("darkgreen","darkorange","steelblue")) +
  theme_AGL
ggsave("Additional/leafcolor_01.png", mp, width = 18, height = 12)
yy <- xx %>% select(Plot, Leaf.Color, Trait, Value) %>%
  filter(Trait %in% c("mean_blue_segmented","mean_excess_green","mean_red_segmented")) %>%
  spread(Trait, Value)
mp <- ggplot(yy, aes(x = mean_blue_segmented, y = mean_red_segmented, color = as.factor(Leaf.Color))) +
  geom_point() +
  theme_AGL
mp
ggsave("Additional/leafcolor_01.png", mp, width = 18, height = 30, dpi = 600)
```





```{r}
library(GGally)
xf<-ro17_f, xh<-ro17_gc.h; xa<-ro17_gc.a ; xv<-ro17_gc.v; xpca<-myPCA
ggCorrTraits <- function(xf, xh, xa, xv, xpca) {
  xh <- xh[[2]] 
  xa <- xa[[2]] 
  xv <- xv[[2]]
  xpca <- xpca
  xx <- bind_rows() %>%
    Group_by(Entry, Trait) %>%
    summarise(Value = mean(Value, na.rm = T))
  # Plot
  ggpairs(xx, mapping = aes(color = Cluster), columns = colnames(xx)[2:ncol(xx)])
}
```

```{r}
unique(ro17_f$Trait)
```


---

## Growing Degree Days

```{r}
# xx <- ro17_gc.v[[3]]
ggGDDCurves <- function(xx, myTitle = NULL, plotType = "Entries") {
  #
  myEnvs <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_env.csv") %>%
    rename(DAP=DaysAfterPlanting) %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt))
  myCoefs <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_tb_pc_raw.csv") %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt))
  #
  xx <- xx %>% mutate(Date = as.Date(Planting.Date) + DAP,
                      Date = as.character(Date)) %>%
    left_join(select(myCoefs, Plot, Expt, Tb), by = c("Plot","Expt")) %>% 
    left_join(select(myEnvs, Expt, DAP, Temp_mean), by = c("Expt","DAP")) %>%
    mutate(GDD = Temp_mean - Tb)
  xx <- xx %>% group_by(Plot, Rep, Entry, Name, Expt) %>% arrange(DAP) %>%
    mutate(CGDD = cumsum(GDD)) %>% ungroup() %>% 
    group_by(Entry, Name, Expt, CGDD) %>%
    summarise(Predicted.Values = mean(Predicted.Values, na.rm = T))
  #
  x1 <- xx %>% filter(Entry %in% c(19,94,107,252))
  if(plotType == "Entries") {
    mp <- ggplot(xx, aes(x = CGDD, y = Predicted.Values, group = Name)) +
      geom_line(alpha = 0.1) +
      geom_line(data = x1, aes(color = Name)) +
      #facet_grid(. ~ Rep) +
      theme_AGL +
      theme(legend.position = "bottom") +
      scale_color_manual(name = NULL, 
                         values = c("darkgreen","darkred","darkblue","steelblue")) +
      labs(title = myTitle)
  }
  if(plotType == "PCA") {
    xx <- xx %>% left_join(select(myPCA, Name, Cluster), by = "Name")
    mp <- ggplot(xx, aes(x = CGDD, y = Predicted.Values, group = Name, color = Cluster)) +
      geom_line(alpha = 0.5) +
      #geom_line(data = x1, aes(color = Name)) +
      facet_wrap(Cluster ~ ., ncol = 4) +
      scale_color_manual(values = myColors_Cluster) +
      theme_AGL +
      labs(title = myTitle)
  }
  mp
}
mp1 <- ggGDDCurves(xx = it17_gc.v[[3]], myTitle = "Italy 2017")
mp2 <- ggGDDCurves(xx = ro17_gc.v[[3]], myTitle = "Rosthern 2017")
mp3 <- ggGDDCurves(xx = su17_gc.v[[3]], myTitle = "Sutherland 2017")
mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
ggsave("Additional/ggGDDCurves_Volume.png", mp, width = 10, height = 4)
#
mp1 <- ggGDDCurves(xx = it17_gc.v[[3]], myTitle = "Italy 2017 Volume")
mp2 <- ggGDDCurves(xx = it17_gc.h[[3]], myTitle = "Height")
mp3 <- ggGDDCurves(xx = it17_gc.a[[3]], myTitle = "Area")
mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
ggsave("Additional/ggGDDCurves_VHA_It17.png", mp, width = 10, height = 4)
#
mp1 <- ggGDDCurves(xx = ro17_gc.v[[3]], myTitle = "Rosthern 2017 Volume")
mp2 <- ggGDDCurves(xx = ro17_gc.h[[3]], myTitle = "Height")
mp3 <- ggGDDCurves(xx = ro17_gc.a[[3]], myTitle = "Area")
mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
ggsave("Additional/ggGDDCurves_VHA_Ro17.png", mp, width = 10, height = 4)
#
mp1 <- ggGDDCurves(xx = su17_gc.v[[3]], myTitle = "Sutherland 2017 Volume")
mp2 <- ggGDDCurves(xx = su17_gc.h[[3]], myTitle = "Height")
mp3 <- ggGDDCurves(xx = su17_gc.a[[3]], myTitle = "Area")
mp <- ggarrange(mp1, mp2, mp3, ncol = 3, common.legend = T)
ggsave("Additional/ggGDDCurves_VHA_Su17.png", mp, width = 10, height = 4)
#
mp <- ggGDDCurves(xx = it17_gc.v[[3]], myTitle = "Italy 2017", plotType = "PCA")
ggsave("Additional/ggGDDCurves_It17_PCA_Volume.png", mp, width = 8, height = 6)
mp <- ggGDDCurves(xx = ro17_gc.v[[3]], myTitle = "Rosthern 2017", plotType = "PCA")
ggsave("Additional/ggGDDCurves_Ro17_PCA_Volume.png", mp, width = 8, height = 6)
mp <- ggGDDCurves(xx = su17_gc.v[[3]], myTitle = "Sutherland 2017", plotType = "PCA")
ggsave("Additional/ggGDDCurves_Su17_PCA_Volume.png", mp, width = 8, height = 6)
```

```{r}
# xx <- ro17_gc.v[[3]]
# xx <- it17_gc.v
# xF <- it17_f
calcGDD <- function(xx, xF) {
  #
  xE <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_env.csv") %>%
    rename(DAP=DaysAfterPlanting) %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt))
  xPT <- read.csv("https://raw.githubusercontent.com/derekmichaelwright/AGILE_LDP_Phenology/master/data/data_tb_pc_raw.csv") %>%
    mutate(Expt = gsub("Metaponto, |Canada |,", "", Expt))
  #
  xF <- xF %>% filter(Trait == "DTF") %>% select(Plot, DTF=Value)
  xC <- xx[[2]] %>% select(Plot, k, x.min, x.mid, x.max) %>%
    left_join(xF, by = "Plot")
  xD <- xx[[3]] %>% mutate(Date = as.Date(Planting.Date) + DAP,
                      Date = as.character(Date)) %>%
    left_join(select(xPT, Plot, Expt, Tb, Pc), by = c("Plot","Expt")) %>% 
    left_join(xC, by = "Plot") %>% 
    left_join(select(xE, Expt, DAP, Temp_mean, DayLength), by = c("Expt","DAP")) %>%
    mutate(GDD = Temp_mean - Tb,
           PPD = DayLength - Pc,
           PTT = GDD * PPD)
  xD <- xD %>% group_by(Plot, Rep, Entry, Name, Expt) %>% arrange(DAP) %>%
    mutate(GDD = cumsum(GDD), PPD = cumsum(PPD), PTT = cumsum(PTT)) %>% 
    ungroup() %>%
    filter(!is.na(Temp_mean))
    #group_by(Entry, Name, Expt, GDD, PPD, PTT) %>%
    #summarise(Predicted.Values = mean(Predicted.Values, na.rm = T))
  #
  xG <- NULL
  #i <- 7072
  for(i in unique(xD$Plot)) {
    xi <- xD %>% filter(Plot == i)
    xi <- xi %>%
      mutate(GDD.min = max(xi %>% filter(DAP <= unique(xi$x.min)) %>% pull(GDD)),
             GDD.mid = max(xi %>% filter(DAP <= unique(xi$x.mid)) %>% pull(GDD)),
             GDD.max = max(xi %>% filter(DAP <= unique(xi$x.max)) %>% pull(GDD)),
             GDD.max.DTF = max(xi %>% filter(DAP <= unique(xi$x.max)) %>% pull(GDD)) -
                            max(xi %>% filter(DAP <= unique(xi$DTF)) %>% pull(GDD)),
             GDD.x.d = GDD.max - GDD.mid,
             
             #
             PPD.min = max(xi %>% filter(DAP <= unique(xi$x.min)) %>% pull(PPD)),
             PPD.mid = max(xi %>% filter(DAP <= unique(xi$x.mid)) %>% pull(PPD)),
             PPD.max = max(xi %>% filter(DAP <= unique(xi$x.max)) %>% pull(PPD)),
             PPD.max.DTF = max(xi %>% filter(DAP <= unique(xi$x.max)) %>% pull(PPD)) -
                            max(xi %>% filter(DAP <= unique(xi$DTF)) %>% pull(PPD)),
             PPD.x.d = PPD.max - PPD.mid,
             #
             PTT.min = max(xi %>% filter(DAP <= unique(xi$x.min)) %>% pull(PTT)),
             PTT.mid = max(xi %>% filter(DAP <= unique(xi$x.mid)) %>% pull(PTT)),
             PTT.max = max(xi %>% filter(DAP <= unique(xi$x.max)) %>% pull(PTT)),
             PTT.max.DTF = max(xi %>% filter(DAP <= unique(xi$x.max)) %>% pull(PTT)) -
                            max(xi %>% filter(DAP <= unique(xi$DTF)) %>% pull(PTT)),
             PTT.x.d = PTT.max - PTT.mid
             )
    xi <- xi %>% slice(1) %>% 
      select(Plot, Entry, Name, Expt,
             GDD.min, GDD.mid, GDD.max, GDD.max.DTF, GDD.x.d,
             PPD.min, PPD.mid, PPD.max, PPD.max.DTF, PPD.x.d,
             PTT.min, PTT.mid, PTT.max, PTT.max.DTF, PTT.x.d
         )
    xG <- bind_rows(xG, xi)
  }
  xG[sapply(xG, is.infinite)] <- NA
  xG
}
#
it17_gdd.v <- calcGDD(xx = it17_gc.v, xF = it17_f)
it17_gdd.h <- calcGDD(xx = it17_gc.h, xF = it17_f)
it17_gdd.a <- calcGDD(xx = it17_gc.a, xF = it17_f)
#
ro17_gdd.v <- calcGDD(xx = ro17_gc.v, xF = ro17_f)
ro17_gdd.h <- calcGDD(xx = ro17_gc.h, xF = ro17_f)
ro17_gdd.a <- calcGDD(xx = ro17_gc.a, xF = ro17_f)
#
su17_gdd.v <- calcGDD(xx = su17_gc.v, xF = su17_f)
su17_gdd.h <- calcGDD(xx = su17_gc.h, xF = su17_f)
su17_gdd.a <- calcGDD(xx = su17_gc.a, xF = su17_f)
#
```

---

# Figure 06

```{r}
xH <- su17_gc.h[[2]]
xA <- su17_gc.a[[2]]
xPCA <- myPCA
xlims <- c(0.4, 2.3)
ylims <- c(0.05, 0.42)
ggHA <- function(xH, xA, xPCA, xlims, ylims) {
  # Prep data
  xH <- xH %>% select(Plot, Entry, Expt, Height=k)
  xA <- xA %>% select(Plot, Entry, Area=k)
  xPCA <- xPCA %>% select(Entry, Cluster)
  xx <- left_join(xH, xA, by = c("Plot","Entry")) %>%
    group_by(Entry, Expt) %>%
    summarise(Height = mean(Height, na.rm = T),
              Area = mean(Area, na.rm = T)) %>%
    ungroup() %>%
    left_join(xPCA, by = "Entry")
  # Plot
  ggplot(xx, aes(x = Area, y = Height, color = Cluster)) +
    geom_point() +
    facet_grid(. ~ Expt) +
    scale_color_manual(values = myColors_Cluster) +
    xlim(xlims) + ylim(ylims) +
    theme_AGL 
}
myxlims <- c(0.4, 2.3)
myylims <- c(0.05, 0.42)
mp1 <- ggHA(xH = it17_gc.h[[2]], xA = it17_gc.a[[2]], 
            xPCA = myPCA, xlims = myxlims, ylims = myylims)
mp2 <- ggHA(xH = ro17_gc.h[[2]], xA = ro17_gc.a[[2]], 
            xPCA = myPCA, xlims = myxlims, ylims = myylims)
mp3 <- ggHA(xH = su17_gc.h[[2]], xA = su17_gc.a[[2]], 
            xPCA = myPCA, xlims = myxlims, ylims = myylims)
mp4 <- ggHA(xH = su18_gc.h[[2]], xA = su18_gc.a[[2]], 
            xPCA = myPCA, xlims = myxlims, ylims = myylims)
mp <- ggarrange(mp1, mp2, mp3, mp4, ncol = 2, nrow = 2,
                common.legend = T, legend = "bottom")
ggsave("Figure_06.png", mp, width = 8, height = 8, dpi = 600, bg = "white")
```

---

&copy; Derek Michael Wright